---
title: "Univariable models"
author: "Mathilde Le Vu"
date: "2024-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Gestational age 
```{r}
  m_GA_u_sev_F<- rlm(GA_weeks_corrected ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Female"))
  summary(m_GA_u_sev_F)
  nobs(m_GA_u_sev_F)

  m_GA_u_sev_M<- rlm(GA_weeks_corrected ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Male"))
  summary(m_GA_u_sev_M)
  nobs(m_GA_u_sev_M)
```

## Table FEMALES
```{r}
GA_GLM3 <- round(head(estimates_cont_rlm(m_GA_u_sev_F)), 2)

  GA_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  GA_GLM3['category'] <- c(" ",
                          "mild", "severe")
  GA_GLM3<-GA_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_GA_gt <- GA_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=986")
    M_GA_gt
    
M_GA_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_GA_severity_univ_F.docx"))
```

## Table MALES
```{r}
GA_GLM3 <- round(head(estimates_cont_rlm(m_GA_u_sev_M)), 2)

  GA_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  GA_GLM3['category'] <- c(" ",
                          "mild", "severe")
  GA_GLM3<-GA_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_GA_gt <- GA_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,051")
    M_GA_gt
    
M_GA_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_GA_severity_univ_M.docx"))
```


## Marginally adjusted means FEMALES
```{r}
m_GA_a_mmeans_f <- ggemmeans(m_GA_u_sev_F, "Grippe_severity3")
m_GA_a_mmeans_f <- mmeans_ci_vertic_cont(m_GA_a_mmeans_f) 

m_GA_a_mmeans_f['outcome'] <- c("gestational age (weeks)")
m_GA_a_mmeans_f['sex'] <- c("females")
m_GA_a_mmeans_f['severity'] <- c("no", "mild", "severe")
m_GA_a_mmeans_f<-m_GA_a_mmeans_f[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_GA_a_mmeans_m <- ggemmeans(m_GA_u_sev_M, "Grippe_severity3")
m_GA_a_mmeans_m <- mmeans_ci_vertic_cont(m_GA_a_mmeans_m) 

m_GA_a_mmeans_m['outcome'] <- c("gestational age (weeks)")
m_GA_a_mmeans_m['sex'] <- c("males")
m_GA_a_mmeans_m['severity'] <- c("no", "mild", "severe")
m_GA_a_mmeans_m<-m_GA_a_mmeans_m[,c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Birthweight 
```{r}
  m_BW_u_sev_F<- rlm(birthweight ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Female"))
  summary(m_BW_u_sev_F)
  nobs(m_BW_u_sev_F)
  m_BW_u_sev_M<- rlm(birthweight ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Male"))
  summary(m_BW_u_sev_M)
  nobs(m_BW_u_sev_M)
```

## Table FEMALES
```{r}
BW_GLM3 <- round(head(estimates_cont_rlm(m_BW_u_sev_F)), 2)

  BW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  BW_GLM3['category'] <- c(" ",
                          "mild", "severe")
  BW_GLM3<-BW_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_BW_gt <- BW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=986")
    M_BW_gt
    
M_BW_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_BW_severity_univ_F.docx"))
```

## Table MALES
```{r}
BW_GLM3 <- round(head(estimates_cont_rlm(m_BW_u_sev_M)), 2)

  BW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  BW_GLM3['category'] <- c(" ",
                          "mild", "severe")
  BW_GLM3<-BW_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_BW_gt <- BW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,051")
    M_BW_gt
    
M_BW_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_BW_severity_univ_M.docx"))
```

## Marginally adjusted means FEMALES
```{r}
m_BW_a_mmeans_f <- ggemmeans(m_BW_u_sev_F, "Grippe_severity3")
m_BW_a_mmeans_f <- mmeans_ci_vertic_cont(m_BW_a_mmeans_f) 

m_BW_a_mmeans_f['outcome'] <- c("birth weight (g)")
m_BW_a_mmeans_f['sex'] <- c("females")
m_BW_a_mmeans_f['severity'] <- c("no", "mild", "severe")
m_BW_a_mmeans_f<-m_BW_a_mmeans_f[,c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_BW_a_mmeans_m <- ggemmeans(m_BW_u_sev_M, "Grippe_severity3")
m_BW_a_mmeans_m <- mmeans_ci_vertic_cont(m_BW_a_mmeans_m) 

m_BW_a_mmeans_m['outcome'] <- c("birth weight (g)")
m_BW_a_mmeans_m['sex'] <- c("males")
m_BW_a_mmeans_m['severity'] <- c("no", "mild", "severe")
m_BW_a_mmeans_m<-m_BW_a_mmeans_m[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Head circumference 
```{r}
  m_HC_sev_F<- rlm(head_circ ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Female"))
summary(m_HC_sev_F)
nobs(m_HC_sev_F)

  m_HC_sev_M<- rlm(head_circ ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Male"))
summary(m_HC_sev_M)
nobs(m_HC_sev_M)
```

## Table FEMALES
```{r}
HC_GLM3 <- round(head(estimates_cont_rlm(m_HC_sev_F)), 2)

  HC_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", "")
  HC_GLM3['category'] <- c(" ",
                          "mild", "severe")
  HC_GLM3 <- HC_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_HC_gt <- HC_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=981")
    M_HC_gt
    
M_HC_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_HC_severity_univ_F.docx"))
```

## Table MALES
```{r}
HC_GLM3 <- round(head(estimates_cont_rlm(m_HC_sev_M)), 2)

  HC_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  HC_GLM3['category'] <- c(" ",
                          "mild", "severe")
  HC_GLM3 <- HC_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_HC_gt <- HC_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,048")
    M_HC_gt
    
M_HC_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_HC_severity_univ_M.docx"))
```

## Marginally adjusted means FEMALES
```{r}
m_HC_a_mmeans_f <- ggemmeans(m_HC_sev_F, "Grippe_severity3")
m_HC_a_mmeans_f <- mmeans_ci_vertic_cont(m_HC_a_mmeans_f) 

m_HC_a_mmeans_f['outcome'] <- c("head circumference (cm)")
m_HC_a_mmeans_f['sex'] <- c("females")
m_HC_a_mmeans_f['severity'] <- c("no", "mild", "severe")
m_HC_a_mmeans_f<-m_HC_a_mmeans_f[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_HC_a_mmeans_m <- ggemmeans(m_HC_sev_M, "Grippe_severity3")
m_HC_a_mmeans_m <- mmeans_ci_vertic_cont(m_HC_a_mmeans_m) 

m_HC_a_mmeans_m['outcome'] <- c("head circumference (cm)")
m_HC_a_mmeans_m['sex'] <- c("males")
m_HC_a_mmeans_m['severity'] <- c("no", "mild", "severe")
m_HC_a_mmeans_m<-m_HC_a_mmeans_m[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Placenta weight 
```{r}
  m_PW_sev_F<- rlm(placentaweight ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Female"))
  summary(m_PW_sev_F)
  nobs(m_PW_sev_F)

  m_PW_sev_M<- rlm(placentaweight ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Male"))
  summary(m_PW_sev_M)
  nobs(m_PW_sev_M)
```

## Table FEMALES
```{r}
PW_GLM3 <- round(head(estimates_cont_rlm(m_PW_sev_F)), 2)

  PW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  PW_GLM3['category'] <- c(" ",
                          "mild", "severe")
  PW_GLM3 <- PW_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PW_gt <- PW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=976")
    M_PW_gt
    
M_PW_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_PW_severity_univ_F.docx"))
```

## Table MALES
```{r}
PW_GLM3 <- round(head(estimates_cont_rlm(m_PW_sev_M)), 2)

  PW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  PW_GLM3['category'] <- c(" ",
                          "mild", "severe")
  PW_GLM3 <- PW_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PW_gt <- PW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,035")
    M_PW_gt
    
M_PW_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_PW_severity_univ_M.docx"))
```

## Marginally adjusted means FEMALES
```{r}
m_PW_a_mmeans_f <- ggemmeans(m_PW_sev_F, "Grippe_severity3")
m_PW_a_mmeans_f <- mmeans_ci_vertic_cont(m_PW_a_mmeans_f) 

m_PW_a_mmeans_f['outcome'] <- c("placenta weight (g)")
m_PW_a_mmeans_f['sex'] <- c("females")
m_PW_a_mmeans_f['severity'] <- c("no", "mild", "severe")
m_PW_a_mmeans_f<-m_PW_a_mmeans_f[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_PW_a_mmeans_m <- ggemmeans(m_PW_sev_M, "Grippe_severity3")
m_PW_a_mmeans_m <- mmeans_ci_vertic_cont(m_PW_a_mmeans_m) 

m_PW_a_mmeans_m['outcome'] <- c("placenta weight (g)")
m_PW_a_mmeans_m['sex'] <- c("males")
m_PW_a_mmeans_m['severity'] <- c("no", "mild", "severe")
m_PW_a_mmeans_m<-m_PW_a_mmeans_m[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Birth length 
```{r}
  m_BL_sev_F<- rlm(babylength ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Female"))
  summary(m_BL_sev_F)
  nobs(m_BL_sev_F)

  m_BL_sev_M<- rlm(babylength ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Male"))
  summary(m_BL_sev_M)
  nobs(m_BL_sev_M)
```

## Table FEMALES
```{r}
BL_GLM3 <- round(head(estimates_cont_rlm(m_BL_sev_F)), 2)

  BL_GLM3['Parameters'] <- c("intercept", 
                           "Flu severity (ref: no flu)", ""
                            )
  BL_GLM3['category'] <- c(" ",
                          "mild", "severe")
  BL_GLM3 <- BL_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_BL_gt <- BL_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=983")
    M_BL_gt
    
M_BL_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_BL_severity_univ_F.docx"))
```

## Table MALES
```{r}
BL_GLM3 <- round(head(estimates_cont_rlm(m_BL_sev_M)), 2)

  BL_GLM3['Parameters'] <- c("intercept", 
                           "Flu severity (ref: no flu)", ""
                            )
  BL_GLM3['category'] <- c(" ",
                          "mild", "severe")
  BL_GLM3 <- BL_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_BL_gt <- BL_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,050")
    M_BL_gt
    
M_BL_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_BL_severity_univ_M.docx"))
```

## Marginally adjusted means FEMALES
```{r}
m_BL_a_mmeans_f <- ggemmeans(m_BL_sev_F, "Grippe_severity3")
m_BL_a_mmeans_f <- mmeans_ci_vertic_cont(m_BL_a_mmeans_f) 

m_BL_a_mmeans_f['outcome'] <- c("birth length (cm)")
m_BL_a_mmeans_f['sex'] <- c("females")
m_BL_a_mmeans_f['severity'] <- c("no", "mild", "severe")
m_BL_a_mmeans_f<-m_BL_a_mmeans_f[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_BL_a_mmeans_m <- ggemmeans(m_BL_sev_M, "Grippe_severity3")
m_BL_a_mmeans_m <- mmeans_ci_vertic_cont(m_BL_a_mmeans_m) 

m_BL_a_mmeans_m['outcome'] <- c("birth length (cm)")
m_BL_a_mmeans_m['sex'] <- c("males")
m_BL_a_mmeans_m['severity'] <- c("no", "mild", "severe")
m_BL_a_mmeans_m<-m_BL_a_mmeans_m[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```


# PI 
```{r}
  m_PI_sev_F<- rlm(PI ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Female"))
  summary(m_PI_sev_F)
  nobs(m_PI_sev_F)

  m_PI_sev_M<- rlm(PI ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Male"))
  summary(m_PI_sev_M)
  nobs(m_PI_sev_M)
```

## Table FEMALES
```{r}
PI_GLM3 <- round(head(estimates_cont_rlm(m_PI_sev_F)), 2)

  PI_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  PI_GLM3['category'] <- c(" ",
                          "mild", "severe")
  PI_GLM3 <- PI_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PI_gt <- PI_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=983")
    M_PI_gt
    
M_PI_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_PI_severity_univ_F.docx"))
```


## Table MALES
```{r}
PI_GLM3 <- round(head(estimates_cont_rlm(m_PI_sev_M)), 2)

  PI_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  PI_GLM3['category'] <- c(" ",
                          "mild", "severe")
  PI_GLM3 <- PI_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PI_gt <- PI_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,050")
    M_PI_gt
    
M_PI_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_PI_severity_univ_M.docx"))
```

## Marginally adjusted means FEMALES
```{r}
m_PI_a_mmeans_f <- ggemmeans(m_PI_sev_F, "Grippe_severity3")
m_PI_a_mmeans_f <- mmeans_ci_vertic_cont(m_PI_a_mmeans_f) 

m_PI_a_mmeans_f['outcome'] <- c("ponderal index")
m_PI_a_mmeans_f['sex'] <- c("females")
m_PI_a_mmeans_f['severity'] <- c("no", "mild", "severe")
m_PI_a_mmeans_f<-m_PI_a_mmeans_f[,c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_PI_a_mmeans_m <- ggemmeans(m_PI_sev_M, "Grippe_severity3")
m_PI_a_mmeans_m <- mmeans_ci_vertic_cont(m_PI_a_mmeans_m) 

m_PI_a_mmeans_m['outcome'] <- c("ponderal index")
m_PI_a_mmeans_m['sex'] <- c("males")
m_PI_a_mmeans_m['severity'] <- c("no", "mild", "severe")
m_PI_a_mmeans_m<-m_PI_a_mmeans_m[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Pooling the tables for predicted means together
```{r}
a_m_cont_outc_u_sev_sex <- rbind(m_BW_a_mmeans_f ,m_BW_a_mmeans_m,
                             m_HC_a_mmeans_f, m_HC_a_mmeans_m,
                             m_PW_a_mmeans_f, m_PW_a_mmeans_m, 
                             m_BL_a_mmeans_f, m_BL_a_mmeans_m,
                             m_PI_a_mmeans_f, m_PI_a_mmeans_m,
                             m_GA_a_mmeans_f, m_GA_a_mmeans_m)
a_m_cont_outc_u_sev_sex <- a_m_cont_outc_u_sev_sex %>%
  mutate(mean=round(mean, 2),
         lci=round(lci, 2),
         uci=round(uci, 2),
         model="univariable")
a_m_cont_outc_u_sev_sex%>%
  gt() %>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity/rlm", "M_cont_estimates_Flu_severity_sex_univ_gt.docx"))
```

# LBW 
```{r}
 m_LBW_sev_F<- glm(LBW ~ Grippe_severity3, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Female"))
  summary(m_LBW_sev_F)
  nobs(m_LBW_sev_F)

 m_LBW_sev_M<- glm(LBW ~ Grippe_severity3, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Male"))
  summary(m_LBW_sev_M)
  nobs(m_LBW_sev_M)
```

## Table FEMALES
```{r}
LBW_GLM3 <- round(head(estimates_binary(m_LBW_sev_F)), 2)

  LBW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  LBW_GLM3['category'] <- c(" ",
                          "mild", "severe")
  LBW_GLM3<-LBW_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_LBW_gt <- LBW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=986")
    M_LBW_gt
    
LBW_estimates_gt <- M_LBW_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity", "M_LBW_severity_univ_F.docx"))
```

## Table MALES
```{r}
LBW_GLM3 <- round(head(estimates_binary(m_LBW_sev_M)), 2)

  LBW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  LBW_GLM3['category'] <- c(" ",
                          "mild", "severe")
  LBW_GLM3<-LBW_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_LBW_gt <- LBW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,051")
    M_LBW_gt
    
LBW_estimates_gt <- M_LBW_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity", "M_LBW_severity_univ_M.docx"))
```

## Marginal proportions females
```{r}
m_LBW_a_mmeans_f <- ggemmeans(m_LBW_sev_F, "Grippe_severity3", margin="marginalmeans")
m_LBW_a_mmeans_f <- mmeans_ci_vertic_bin(m_LBW_a_mmeans_f) 

m_LBW_a_mmeans_f['outcome'] <- c("LBW (<2,500g)")
m_LBW_a_mmeans_f['sex'] <- c("females")
m_LBW_a_mmeans_f['severity'] <- c("no", "mild", "severe")
m_LBW_a_mmeans_f<-m_LBW_a_mmeans_f[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginal proportions males
```{r}
m_LBW_a_mmeans_m <- ggemmeans(m_LBW_sev_M, "Grippe_severity3", margin="marginalmeans")
m_LBW_a_mmeans_m <- mmeans_ci_vertic_bin(m_LBW_a_mmeans_m) 

m_LBW_a_mmeans_m['outcome'] <- c("LBW (<2,500g)")
m_LBW_a_mmeans_m['sex'] <- c("males")
m_LBW_a_mmeans_m['severity'] <- c("no", "mild", "severe")
m_LBW_a_mmeans_m<-m_LBW_a_mmeans_m[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Stillbirth 
```{r}
m_SB_sev_F<- glm(stillbirth ~ Grippe_severity3, family = binomial, data=flu_cases_during_pregn_pandemy_sev, subset=(sex=="Female"))
  summary(m_SB_sev_F)
  nobs(m_SB_sev_F)
  
m_SB_sev_M<- glm(stillbirth ~ Grippe_severity3, family = binomial, data=flu_cases_during_pregn_pandemy_sev, subset=(sex=="Male"))
  summary(m_SB_sev_M)
  nobs(m_SB_sev_M)
```

## Table FEMALES
```{r}
SB_GLM3 <- round(head(estimates_binary(m_SB_sev_F)), 2)

  SB_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  SB_GLM3['category'] <- c(" ",
                          "mild", "severe")
  SB_GLM3<-SB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_SB_gt <- SB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,023")
    M_SB_gt
    
SB_estimates_gt <- M_SB_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity", "M_SB_severity_univ_F.docx"))
```

## Table MALES
```{r}
SB_GLM3 <- round(head(estimates_binary(m_SB_sev_M)), 2)

  SB_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  SB_GLM3['category'] <- c(" ",
                          "mild", "severe")
  SB_GLM3<-SB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_SB_gt <- SB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,104")
    M_SB_gt
    
SB_estimates_gt <- M_SB_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity", "M_SB_severity_univ_M.docx"))
```

## Marginal proportions females
```{r}
m_SB_a_mmeans_f <- ggemmeans(m_SB_sev_F, "Grippe_severity3", margin="marginalmeans")
m_SB_a_mmeans_f <- mmeans_ci_vertic_bin(m_SB_a_mmeans_f) 

m_SB_a_mmeans_f['outcome'] <- c("stillbirth")
m_SB_a_mmeans_f['sex'] <- c("females")
m_SB_a_mmeans_f['severity'] <- c("no", "mild", "severe")
m_SB_a_mmeans_f<-m_SB_a_mmeans_f[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginal proportions males
```{r}
m_SB_a_mmeans_m <- ggemmeans(m_SB_sev_M, "Grippe_severity3", margin="marginalmeans")
m_SB_a_mmeans_m <- mmeans_ci_vertic_bin(m_SB_a_mmeans_m) 

m_SB_a_mmeans_m['outcome'] <- c("stillbirth")
m_SB_a_mmeans_m['sex'] <- c("males")
m_SB_a_mmeans_m['severity'] <- c("no", "mild", "severe")
m_SB_a_mmeans_m<-m_SB_a_mmeans_m[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# PTB 
```{r}
 m_PTB_sev_F<- glm(PTB_corrected ~ Grippe_severity3, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Female"))
  summary(m_PTB_sev_F)
  nobs(m_PTB_sev_F)
 m_PTB_sev_M<- glm(PTB_corrected ~ Grippe_severity3, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Male"))
  summary(m_PTB_sev_M)
  nobs(m_PTB_sev_M)
```

## Table FEMALES
```{r}
PTB_GLM3 <- round(head(estimates_binary(m_PTB_sev_F)), 2)

  PTB_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  PTB_GLM3['category'] <- c(" ",
                          "mild", "severe")
  PTB_GLM3<-PTB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_PTB_gt <- PTB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=986")
    M_PTB_gt
    
PTB_estimates_gt <- M_PTB_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity", "M_PTB_severity_univ_F.docx"))
```

## Table MALES
```{r}
PTB_GLM3 <- round(head(estimates_binary(m_PTB_sev_M)), 2)

  PTB_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  PTB_GLM3['category'] <- c(" ",
                          "mild", "severe")
  PTB_GLM3<-PTB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_PTB_gt <- PTB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,051")
    M_PTB_gt
    
PTB_estimates_gt <- M_PTB_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity", "M_PTB_severity_univ_M.docx"))
```

## Marginal proportions females
```{r}
m_PTB_a_mmeans_f <- ggemmeans(m_PTB_sev_F, "Grippe_severity3", margin="marginalmeans")
m_PTB_a_mmeans_f <- mmeans_ci_vertic_bin(m_PTB_a_mmeans_f) 

m_PTB_a_mmeans_f['outcome'] <- c("PTB (<37 weeks)")
m_PTB_a_mmeans_f['sex'] <- c("females")
m_PTB_a_mmeans_f['severity'] <- c("no", "mild", "severe")
m_PTB_a_mmeans_f<-m_PTB_a_mmeans_f[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginal proportions males
```{r}
m_PTB_a_mmeans_m <- ggemmeans(m_PTB_sev_M, "Grippe_severity3", margin="marginalmeans")
m_PTB_a_mmeans_m <- mmeans_ci_vertic_bin(m_PTB_a_mmeans_m) 

m_PTB_a_mmeans_m['outcome'] <- c("PTB (<37 weeks)")
m_PTB_a_mmeans_m['sex'] <- c("males")
m_PTB_a_mmeans_m['severity'] <-  c("no", "mild", "severe")
m_PTB_a_mmeans_m<-m_PTB_a_mmeans_m[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Neonat mortality
```{r}
 m_NM_sev_F<- glm(neonat_mort_d1_d5 ~ Grippe_severity3, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Female"))
  summary(m_NM_sev_F)
  nobs(m_NM_sev_F)
 m_NM_sev_M<- glm(neonat_mort_d1_d5 ~ Grippe_severity3, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths, subset=(sex=="Male"))
  summary(m_NM_sev_M)
  nobs(m_NM_sev_M)
```

## Table FEMALES
```{r}
NM_GLM3 <- round(head(estimates_binary(m_NM_sev_F)), 2)

  NM_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  NM_GLM3['category'] <- c(" ",
                          "mild", "severe")
  NM_GLM3<-NM_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_NM_gt <- NM_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  )%>%
     tab_source_note(source_note = "n=985")
    M_NM_gt
    
NM_estimates_gt <- M_NM_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity", "M_NM_severity_univ_F.docx"))
```


## Table MALES
```{r}
NM_GLM_flu_mod <- round(head(estimates_binary(m_NM_sev_M)), 2)

  NM_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  NM_GLM3['category'] <- c(" ",
                          "mild", "severe")
  NM_GLM3<-NM_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_NM_gt <- NM_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  )%>%
     tab_source_note(source_note = "n=1,051")
    M_NM_gt
    
NM_estimates_gt <- M_NM_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity", "M_NM_severity_univ_M.docx"))
```

## Marginal proportions females
```{r}
m_NM_a_mmeans_f <- ggemmeans(m_NM_sev_F, "Grippe_severity3", margin="marginalmeans")
m_NM_a_mmeans_f <- mmeans_ci_vertic_bin(m_NM_a_mmeans_f) 

m_NM_a_mmeans_f['outcome'] <- c("early neonatal mortality")
m_NM_a_mmeans_f['sex'] <- c("females")
m_NM_a_mmeans_f['severity'] <- c("no", "mild", "severe")
m_NM_a_mmeans_f<-m_NM_a_mmeans_f[,c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginal proportions males
```{r}
m_NM_a_mmeans_m <- ggemmeans(m_NM_sev_M, "Grippe_severity3", margin="marginalmeans")
m_NM_a_mmeans_m <- mmeans_ci_vertic_bin(m_NM_a_mmeans_m) 

m_NM_a_mmeans_m['outcome'] <- c("early neonatal mortality")
m_NM_a_mmeans_m['sex'] <- c("males")
m_NM_a_mmeans_m['severity'] <-  c("no", "mild", "severe")
m_NM_a_mmeans_m<-m_NM_a_mmeans_m[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```



# Pooling the tables for marginal proportions
```{r}
a_m_bin_outc_u_sev_sex <- rbind(m_LBW_a_mmeans_f, m_LBW_a_mmeans_m,
                            m_PTB_a_mmeans_f,m_PTB_a_mmeans_m
                            #,m_SB_a_mmeans_f, m_SB_a_mmeans_m
                            #,m_NM_a_mmeans_f, m_NM_a_mmeans_m
                            )
a_m_bin_outc_u_sev_sex <- a_m_bin_outc_u_sev_sex %>%
  mutate(mean=round(mean, 4),
         lci=round(lci, 4),
         uci=round(uci, 4),
         model="univariable")
a_m_bin_outc_u_sev_sex%>%
  gt() %>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/sex_stratif/severity", "M_bin_marg_prop_Flu_severity_univ_sex_gt.docx"))
```
