---
title: "Univariable models"
author: "Mathilde Le Vu"
date: "2024-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Gestational age 
```{r}
  m_GA_f_u<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset=(sex=="Female"))
  summary(m_GA_f_u)
  nobs(m_GA_f_u)

  m_GA_m_u<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset=(sex=="Male"))
  summary(m_GA_m_u)
  nobs(m_GA_m_u)
```

## Table FEMALES
```{r}
GA_GLM_flu_mod <- round(head(estimates_cont_rlm(m_GA_f_u)), 2)

  GA_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  GA_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  GA_GLM_flu_mod<-GA_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_GA_gt <- GA_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,013")
    M_GA_gt
    
M_GA_gt%>%
  gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_GA_estimates_Flu_in_pregn_and_in_pandemic_gt_F.docx"))
```

## Table MALES
```{r}
GA_GLM_flu_mod <- round(head(estimates_cont_rlm(m_GA_m_u)), 2)

  GA_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  GA_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  GA_GLM_flu_mod<-GA_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_GA_gt <- GA_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,069")
    M_GA_gt
    
M_GA_gt%>%
   gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_GA_estimates_Flu_in_pregn_and_in_pandemic_gt_M.docx"))
```

## Marginally adjusted means FEMALES
```{r}
m_GA_a_mmeans_f <- ggemmeans(m_GA_f_u, "Flu_in_pregn_and_in_pandemic")
a_m_GA_u_f <- mmeans_ci_vertic_cont(m_GA_a_mmeans_f) 

a_m_GA_u_f['outcome'] <- c("gestational age (weeks)")
a_m_GA_u_f['sex'] <- c("females")
a_m_GA_u_f['flu exp'] <- c("no", "yes")
a_m_GA_u_f<-a_m_GA_u_f[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_GA_a_mmeans_m <- ggemmeans(m_GA_m_u, "Flu_in_pregn_and_in_pandemic")
a_m_GA_u_m <- mmeans_ci_vertic_cont(m_GA_a_mmeans_m) 

a_m_GA_u_m['outcome'] <- c("gestational age (weeks)")
a_m_GA_u_m['sex'] <- c("males")
a_m_GA_u_m['flu exp'] <- c("no", "yes")
a_m_GA_u_m<-a_m_GA_u_m[,c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Birthweight 
```{r}
  m_BW_f_u<- rlm(birthweight ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset=(sex=="Female"))
  summary(m_BW_f_u)
  nobs(m_BW_f_u)

  m_BW_m_u<- rlm(birthweight ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset=(sex=="Male"))
  summary(m_BW_m_u)
  nobs(m_BW_m_u)
```

## Table FEMALES
```{r}
BW_GLM_flu_mod <- round(head(estimates_cont_rlm(m_BW_f_u)), 2)

  BW_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  BW_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  BW_GLM_flu_mod<-BW_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_BW_gt <- BW_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,013")
    M_BW_gt
    
M_BW_gt%>%
  gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_BW_estimates_Flu_in_pregn_and_in_pandemic_gt_F.docx"))
```

## Table MALES
```{r}
BW_GLM_flu_mod <- round(head(estimates_cont_rlm(m_BW_m_u)), 2)

  BW_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  BW_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  BW_GLM_flu_mod<-BW_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_BW_gt <- BW_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,069")
    M_BW_gt
    
M_BW_gt%>%
  gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_BW_estimates_Flu_in_pregn_and_in_pandemic_gt_M.docx"))
```
## Marginally adjusted means FEMALES
```{r}
m_BW_a_mmeans_f <- ggemmeans(m_BW_f_u, "Flu_in_pregn_and_in_pandemic")
a_m_BW_u_f <- mmeans_ci_vertic_cont(m_BW_a_mmeans_f) 

a_m_BW_u_f['outcome'] <- c("birth weight (g)")
a_m_BW_u_f['sex'] <- c("females")
a_m_BW_u_f['flu exp'] <- c("no", "yes")
a_m_BW_u_f<-a_m_BW_u_f[,c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_BW_a_mmeans_m <- ggemmeans(m_BW_m_u, "Flu_in_pregn_and_in_pandemic")
a_m_BW_u_m <- mmeans_ci_vertic_cont(m_BW_a_mmeans_m) 

a_m_BW_u_m['outcome'] <- c("birth weight (g)")
a_m_BW_u_m['sex'] <- c("males")
a_m_BW_u_m['flu exp'] <- c("no", "yes")
a_m_BW_u_m<-a_m_BW_u_m[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Head circumference 
```{r}
m_HC_f_u<- rlm(head_circ ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset = (sex=="Female"))
summary(m_HC_f_u)
nobs(m_HC_f_u)

m_HC_m_u<- rlm(head_circ ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset = (sex=="Male"))
summary(m_HC_m_u)
nobs(m_HC_m_u)
```

## Table FEMALES
```{r}
HC_GLM_flu_mod <- round(head(estimates_cont_rlm(m_HC_f_u)), 2)

  HC_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  HC_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  HC_GLM_flu_mod <- HC_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_HC_gt <- HC_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,008")
    M_HC_gt
    
M_HC_gt%>%
    gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm",
              "M_HC_estimates_Flu_in_pregn_and_in_pandemic_gt_F.docx"))
```

## Table MALES
```{r}
HC_GLM_flu_mod <- round(head(estimates_cont_rlm(m_HC_m_u)), 2)

  HC_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  HC_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  HC_GLM_flu_mod <- HC_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_HC_gt <- HC_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,066")
    M_HC_gt
    
M_HC_gt%>%
   gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm",
              "M_HC_estimates_Flu_in_pregn_and_in_pandemic_gt_M.docx"))
```

## Marginally adjusted means FEMALES
```{r}
m_HC_a_mmeans_f <- ggemmeans(m_HC_f_u, "Flu_in_pregn_and_in_pandemic")
a_m_HC_u_f <- mmeans_ci_vertic_cont(m_HC_a_mmeans_f) 

a_m_HC_u_f['outcome'] <- c("head circumference (cm)")
a_m_HC_u_f['sex'] <- c("females")
a_m_HC_u_f['flu exp'] <- c("no", "yes")
a_m_HC_u_f<-a_m_HC_u_f[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_HC_a_mmeans_m <- ggemmeans(m_HC_m_u, "Flu_in_pregn_and_in_pandemic")
a_m_HC_u_m <- mmeans_ci_vertic_cont(m_HC_a_mmeans_m) 

a_m_HC_u_m['outcome'] <- c("head circumference (cm)")
a_m_HC_u_m['sex'] <- c("males")
a_m_HC_u_m['flu exp'] <- c("no", "yes")
a_m_HC_u_m<-a_m_HC_u_m[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Placenta weight 
```{r}
  m_PW_f_u<- rlm(placentaweight ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset=(sex=="Female"))
  summary(m_PW_f_u)
  nobs(m_PW_f_u)

  m_PW_m_u <- rlm(placentaweight ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset=(sex=="Male"))
  summary(m_PW_m_u)
  nobs(m_PW_m_u)
```

## Table FEMALES
```{r}
PW_GLM_flu_mod <- round(head(estimates_cont_rlm(m_PW_f_u)), 2)

  PW_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  PW_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  PW_GLM_flu_mod <- PW_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_PW_gt <- PW_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,003")
    M_PW_gt
    
M_PW_gt%>%
   gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_PW_estimates_Flu_in_pregn_and_in_pandemic_gt_F.docx"))
```

## Table MALES
```{r}
PW_GLM_flu_mod <- round(head(estimates_cont_rlm(m_PW_m_u)), 2)

  PW_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  PW_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  PW_GLM_flu_mod <- PW_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_PW_gt <- PW_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,053")
    M_PW_gt
    
M_PW_gt%>%
    gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_PW_estimates_Flu_in_pregn_and_in_pandemic_gt_M.docx"))
```

## Marginally adjusted means FEMALES
```{r}
m_PW_a_mmeans_f <- ggemmeans(m_PW_f_u, "Flu_in_pregn_and_in_pandemic")
a_m_PW_u_f <- mmeans_ci_vertic_cont(m_PW_a_mmeans_f) 

a_m_PW_u_f['outcome'] <- c("placenta weight (g)")
a_m_PW_u_f['sex'] <- c("females")
a_m_PW_u_f['flu exp'] <- c("no", "yes")
a_m_PW_u_f<-a_m_PW_u_f[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_PW_a_mmeans_m <- ggemmeans(m_PW_m_u, "Flu_in_pregn_and_in_pandemic")
a_m_PW_u_m <- mmeans_ci_vertic_cont(m_PW_a_mmeans_m) 

a_m_PW_u_m['outcome'] <- c("placenta weight (g)")
a_m_PW_u_m['sex'] <- c("males")
a_m_PW_u_m['flu exp'] <- c("no", "yes")
a_m_PW_u_m<-a_m_PW_u_m[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```


# Birth length 
```{r}
  m_BL_f_u<- rlm(babylength ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset = (sex=="Female"))
  summary(m_BL_f_u)
  nobs(m_BL_f_u)
  
  m_BL_m_u<- rlm(babylength ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset = (sex=="Male"))
  summary(m_BL_m_u)
  nobs(m_BL_m_u)
```

## Table FEMALES
```{r}
BL_GLM_flu_mod <- round(head(estimates_cont_rlm(m_BL_f_u)), 2)

  BL_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  BL_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  BL_GLM_flu_mod <- BL_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_BL_gt <- BL_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,010")
    M_BL_gt
    
M_BL_gt%>%
   gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_BL_estimates_Flu_in_pregn_and_in_pandemic_gt_F.docx"))
```
## Table MALES
```{r}
BL_GLM_flu_mod <- round(head(estimates_cont_rlm(m_BL_m_u)), 2)

  BL_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  BL_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  BL_GLM_flu_mod <- BL_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_BL_gt <- BL_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,068")
    M_BL_gt
    
M_BL_gt%>%
    gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_BL_estimates_Flu_in_pregn_and_in_pandemic_gt_M.docx"))
```

## Marginally adjusted means FEMALES
```{r}
m_BL_a_mmeans_f <- ggemmeans(m_BL_f_u, "Flu_in_pregn_and_in_pandemic")
a_m_BL_u_f <- mmeans_ci_vertic_cont(m_BL_a_mmeans_f) 

a_m_BL_u_f['outcome'] <- c("birth length (cm)")
a_m_BL_u_f['sex'] <- c("females")
a_m_BL_u_f['flu exp'] <- c("no", "yes")
a_m_BL_u_f<-a_m_BL_u_f[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_BL_a_mmeans_m <- ggemmeans(m_BL_m_u, "Flu_in_pregn_and_in_pandemic")
a_m_BL_u_m <- mmeans_ci_vertic_cont(m_BL_a_mmeans_m) 

a_m_BL_u_m['outcome'] <- c("birth length (cm)")
a_m_BL_u_m['sex'] <- c("males")
a_m_BL_u_m['flu exp'] <- c("no", "yes")
a_m_BL_u_m<-a_m_BL_u_m[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# PI 
```{r}
  m_PI_f_u<- rlm(PI ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset=(sex=="Female"))
  summary(m_PI_f_u)
  nobs(m_PI_f_u)

  m_PI_m_u<- rlm(PI ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths, subset=(sex=="Male"))
  summary(m_PI_m_u)
  nobs(m_PI_m_u)
```

## Table FEMALES
```{r}
PI_GLM_flu_mod <- round(head(estimates_cont_rlm(m_PI_f_u)), 2)

  PI_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  PI_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  PI_GLM_flu_mod <- PI_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_PI_gt <- PI_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,010")
    M_PI_gt
    
M_PI_gt%>%
   gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_PI_estimates_Flu_in_pregn_and_in_pandemic_gt_F.docx"))
```
## Table MALES
```{r}
PI_GLM_flu_mod <- round(head(estimates_cont_rlm(m_PI_m_u)), 2)

  PI_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  PI_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  PI_GLM_flu_mod <- PI_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_PI_gt <- PI_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,068")
    M_PI_gt
    
M_PI_gt%>%
    gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_PI_estimates_Flu_in_pregn_and_in_pandemic_gt_M.docx"))
```

## Marginally adjusted means FEMALES
```{r}
m_PI_a_mmeans_f <- ggemmeans(m_PI_f_u, "Flu_in_pregn_and_in_pandemic")
a_m_PI_u_f <- mmeans_ci_vertic_cont(m_PI_a_mmeans_f) 

a_m_PI_u_f['outcome'] <- c("ponderal index")
a_m_PI_u_f['sex'] <- c("females")
a_m_PI_u_f['flu exp'] <- c("no", "yes")
a_m_PI_u_f<-a_m_PI_u_f[,c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginally adjusted means MALES
```{r}
m_PI_a_mmeans_m <- ggemmeans(m_PI_m_u, "Flu_in_pregn_and_in_pandemic")
a_m_PI_u_m <- mmeans_ci_vertic_cont(m_PI_a_mmeans_m) 

a_m_PI_u_m['outcome'] <- c("ponderal index")
a_m_PI_u_m['sex'] <- c("males")
a_m_PI_u_m['flu exp'] <- c("no", "yes")
a_m_PI_u_m<-a_m_PI_u_m[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# Pooling the tables for predicted means together
```{r}
a_m_cont_outc_u_sex <- rbind(a_m_BW_u_f, a_m_BW_u_m, a_m_HC_u_f, a_m_HC_u_m,
                         a_m_PW_u_f, a_m_PW_u_m, a_m_BL_u_f, a_m_BL_u_m,
                         a_m_PI_u_f, a_m_PI_u_m, a_m_GA_u_f, a_m_GA_u_m)
a_m_cont_outc_u_sex <- a_m_cont_outc_u_sex %>%
  mutate(mean=round(mean, 2),
         lci=round(lci, 2),
         uci=round(uci, 2),
         model="univariable")
a_m_cont_outc_u_sex%>%
  gt() %>%
  gtsave(here("output/tables/main_models/sex_stratif/univariable/rlm", "M_cont_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

# LBW 
```{r}
 m_LBW_f_u<- glm(LBW ~ Flu_in_pregn_and_in_pandemic, family = "binomial", data=pandemy_livebirths, subset=(sex=="Female"))
  summary(m_LBW_f_u)
  nobs(m_LBW_f_u)

 m_LBW_m_u<- glm(LBW ~ Flu_in_pregn_and_in_pandemic, family = "binomial", data=pandemy_livebirths, subset=(sex=="Male"))
  summary(m_LBW_m_u)
  nobs(m_LBW_m_u)
```

## Table FEMALES
```{r}
LBW_GLM3 <- round(head(estimates_binary(m_LBW_f_u)), 2)

  LBW_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  LBW_GLM3['category'] <- c(" ",
                          "yes")
  LBW_GLM3<-LBW_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_LBW_gt <- LBW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,013")
    M_LBW_gt
    
LBW_estimates_gt <- M_LBW_gt%>%
    gtsave(here("output/tables/main_models/sex_stratif/univariable", "M_LBW_estimates_Flu_in_pregn_and_in_pandemic_gt_F.docx"))
```

## Table MALES
```{r}
LBW_GLM3 <- round(head(estimates_binary(m_LBW_m_u)), 2)

  LBW_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  LBW_GLM3['category'] <- c(" ",
                          "yes")
  LBW_GLM3<-LBW_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_LBW_gt <- LBW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,069")
    M_LBW_gt
    
LBW_estimates_gt <- M_LBW_gt%>%
    gtsave(here("output/tables/main_models/sex_stratif/univariable", "M_LBW_estimates_Flu_in_pregn_and_in_pandemic_gt_M.docx"))
```

## Marginal proportions females
```{r}
m_LBW_a_mmeans_f <- ggemmeans(m_LBW_f_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
a_m_LBW_u_f <- mmeans_ci_vertic_bin(m_LBW_a_mmeans_f) 

a_m_LBW_u_f['outcome'] <- c("LBW (<2,500g)")
a_m_LBW_u_f['sex'] <- c("females")
a_m_LBW_u_f['flu exp'] <- c("no", "yes")
a_m_LBW_u_f<-a_m_LBW_u_f[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginal proportions males
```{r}
m_LBW_a_mmeans_m <- ggemmeans(m_LBW_m_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
a_m_LBW_u_m <- mmeans_ci_vertic_bin(m_LBW_a_mmeans_m) 

a_m_LBW_u_m['outcome'] <- c("LBW (<2,500g)")
a_m_LBW_u_m['sex'] <- c("males")
a_m_LBW_u_m['flu exp'] <- c("no", "yes")
a_m_LBW_u_m<-a_m_LBW_u_m[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

# stillbirth 
```{r}
 m_SB_f_u<- glm(stillbirth ~ Flu_in_pregn_and_in_pandemic, family = binomial, data=pandemy, subset=(sex=="Female"))
  summary(m_SB_f_u)
  nobs(m_SB_f_u)

 m_SB_m_u<- glm(stillbirth ~ Flu_in_pregn_and_in_pandemic, family = binomial, data=pandemy, subset=(sex=="Male"))
  summary(m_SB_m_u)
  nobs(m_SB_m_u)
```

## Table FEMALES
```{r}
SB_GLM3 <- round(head(estimates_binary(m_SB_f_u)), 2)

  SB_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  SB_GLM3['category'] <- c(" ",
                          "yes")
  SB_GLM3<-SB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_SB_gt <- SB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,050")
    M_SB_gt
    
SB_estimates_gt <- M_SB_gt%>%
    gtsave(here("output/tables/main_models/sex_stratif/univariable", "M_SB_estimates_Flu_in_pregn_and_in_pandemic_gt_F.docx"))
```

### Table MALES
```{r}
SB_GLM3 <- round(head(estimates_binary(m_SB_m_u)), 2)

  SB_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  SB_GLM3['category'] <- c(" ",
                          "yes")
  SB_GLM3<-SB_GLM3[, c('Parameters', "category", "OR", "lci","uci", "pvalue")]

   M_SB_gt <- SB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,122")
    M_SB_gt
    
SB_estimates_gt <- M_SB_gt%>%
    gtsave(here("output/tables/main_models/sex_stratif/univariable", "M_SB_estimates_Flu_in_pregn_and_in_pandemic_gt_M.docx"))
```

## Marginal proportions females
```{r}
m_SB_a_mmeans_f <- ggemmeans(m_SB_f_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
a_m_SB_u_f <- mmeans_ci_vertic_bin(m_SB_a_mmeans_f) 

a_m_SB_u_f['outcome'] <- c("stillbirth")
a_m_SB_u_f['sex'] <- c("females")
a_m_SB_u_f['flu exp'] <- c("no", "yes")
a_m_SB_u_f<-a_m_SB_u_f[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginal proportions males
```{r}
m_SB_a_mmeans_m <- ggemmeans(m_SB_m_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
a_m_SB_u_m <- mmeans_ci_vertic_bin(m_SB_a_mmeans_m) 

a_m_SB_u_m['outcome'] <- c("stillbirth")
a_m_SB_u_m['sex'] <- c("males")
a_m_SB_u_m['flu exp'] <- c("no", "yes")
a_m_SB_u_m<-a_m_SB_u_m[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## PTB 
```{r}
 m_PTB_f_u<- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic, family = "binomial", data=pandemy_livebirths, subset = (sex=="Female"))
  summary(m_PTB_f_u)
  nobs(m_PTB_f_u)

 m_PTB_m_u <- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic, family = "binomial", data=pandemy_livebirths, subset = (sex=="Male"))
  summary(m_PTB_m_u)
  nobs(m_PTB_m_u)
```

### Table FEMALES
```{r}
PTB_GLM3 <- round(head(estimates_binary(m_PTB_f_u)), 2)

  PTB_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  PTB_GLM3['category'] <- c(" ",
                          "yes")
  PTB_GLM3<-PTB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_PTB_gt <- PTB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,013")
    M_PTB_gt
    
PTB_estimates_gt <- M_PTB_gt%>%
   gtsave(here("output/tables/main_models/sex_stratif/univariable", "M_PTB_estimates_Flu_in_pregn_and_in_pandemic_gt_F.docx"))
```

### Table MALES
```{r}
PTB_GLM3 <- round(head(estimates_binary(m_PTB_m_u)), 2)

  PTB_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  PTB_GLM3['category'] <- c(" ",
                          "yes")
  PTB_GLM3<-PTB_GLM3[, c('Parameters', "category", "OR", "lci","uci", "pvalue")]

   M_PTB_gt <- PTB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,069")
    M_PTB_gt
    
PTB_estimates_gt <- M_PTB_gt%>%
    gtsave(here("output/tables/main_models/sex_stratif/univariable", "M_PTB_estimates_Flu_in_pregn_and_in_pandemic_gt_M.docx"))
```

## Marginal proportions females
```{r}
m_PTB_a_mmeans_f <- ggemmeans(m_PTB_f_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
a_m_PTB_u_f <- mmeans_ci_vertic_bin(m_PTB_a_mmeans_f) 

a_m_PTB_u_f['outcome'] <- c("PTB (<37 weeks)")
a_m_PTB_u_f['sex'] <- c("females")
a_m_PTB_u_f['flu exp'] <- c("no", "yes")
a_m_PTB_u_f<-a_m_PTB_u_f[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginal proportions males
```{r}
m_PTB_a_mmeans_m <- ggemmeans(m_PTB_m_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
a_m_PTB_u_m <- mmeans_ci_vertic_bin(m_PTB_a_mmeans_m) 

a_m_PTB_u_m['outcome'] <- c("PTB (<37 weeks)")
a_m_PTB_u_m['sex'] <- c("males")
a_m_PTB_u_m['flu exp'] <- c("no", "yes")
a_m_PTB_u_m<-a_m_PTB_u_m[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```


## Neonat mortality
```{r}
 m_NM_f_u<- glm(neonat_mort_d1_d5 ~ Flu_in_pregn_and_in_pandemic, family = "binomial", data=pandemy_livebirths, subset=(sex=="Female"))
  summary(m_NM_f_u)
  nobs(m_NM_f_u)

m_NM_m_u<- glm(neonat_mort_d1_d5 ~ Flu_in_pregn_and_in_pandemic, family = "binomial", data=pandemy_livebirths, subset=(sex=="Male"))
  summary(m_NM_m_u)
  nobs(m_NM_m_u)
```

### Table FEMALES
```{r}
NM_GLM3 <- round(head(estimates_binary(m_NM_f_u)), 2)

  NM_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  NM_GLM3['category'] <- c(" ",
                          "yes")
  NM_GLM3<-NM_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_NM_gt <- NM_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  )%>%
     tab_source_note(source_note = "n=1,012")
    M_NM_gt
    
NM_estimates_gt <- M_NM_gt%>%
    gtsave(here("output/tables/main_models/sex_stratif/univariable", "M_NM_estimates_Flu_in_pregn_and_in_pandemic_gt_F.docx"))
```

### Table MALES
```{r}
NM_GLM3 <- round(head(estimates_binary(m_NM_m_u)), 2)

  NM_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  NM_GLM3['category'] <- c(" ",
                          "yes")
  NM_GLM3<-NM_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_NM_gt <- NM_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  )%>%
     tab_source_note(source_note = "n=1,069")
    M_NM_gt
    
NM_estimates_gt <- M_NM_gt%>%
   gtsave(here("output/tables/main_models/sex_stratif/univariable", "M_NM_estimates_Flu_in_pregn_and_in_pandemic_gt_M.docx"))
```

## Marginal proportions females
```{r}
m_NM_a_mmeans_f <- ggemmeans(m_NM_f_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
a_m_NM_u_f <- mmeans_ci_vertic_bin(m_NM_a_mmeans_f) 

a_m_NM_u_f['outcome'] <- c("early neonatal mortality")
a_m_NM_u_f['sex'] <- c("females")
a_m_NM_u_f['flu exp'] <- c("no", "yes")
a_m_NM_u_f<-a_m_NM_u_f[,c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```

## Marginal proportions males
```{r}
m_NM_a_mmeans_m <- ggemmeans(m_NM_m_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
a_m_NM_u_m <- mmeans_ci_vertic_bin(m_NM_a_mmeans_m) 

a_m_NM_u_m['outcome'] <- c("early neonatal mortality")
a_m_NM_u_m['sex'] <- c("males")
a_m_NM_u_m['flu exp'] <- c("no", "yes")
a_m_NM_u_m<-a_m_NM_u_m[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff", "sex")]
```



# Pooling the tables for marginal proportions
```{r}
a_m_bin_outc_u_sex <- rbind(a_m_LBW_u_f, a_m_LBW_u_m, a_m_PTB_u_f, a_m_PTB_u_m,
                         a_m_SB_u_f, a_m_SB_u_m, a_m_NM_u_f,a_m_NM_u_m)
a_m_bin_outc_u_sex <- a_m_bin_outc_u_sex %>%
  mutate(mean=round(mean, 4),
         lci=round(lci, 4),
         uci=round(uci, 4),
         model="univariable")
a_m_bin_outc_u_sex%>%
  gt() %>%
  gtsave(here("output/tables/main_models/sex_stratif/univariable", "M_bin_marg_prop_Flu_in_pregn_and_in_pandemic_gt.docx"))
```
