---
title: "Univariable models"
author: "Mathilde Le Vu"
date: "2024-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Gestational age 
```{r}
  m_GA_a<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season, data=pandemy_livebirths)
  summary(m_GA_a)
  
#adding variables one at a time
  #morphology
  m_GA_b<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology, data=pandemy_livebirths)
  AIC(m_GA_b)-AIC(m_GA_a) 
  #morphology improves model fit
  
  # civil status
  m_GA_c<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2, data=pandemy_livebirths)
   AIC(m_GA_c)-AIC(m_GA_b) 
  #civil status improves model fit

   # living inside Lausanne
  m_GA_d<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=pandemy_livebirths)
  AIC(m_GA_d)-AIC(m_GA_c) 
  # Lausanne improves model fit
  
   # HISCO class
  m_GA_e<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+hisco_class_3, data=pandemy_livebirths)
  AIC(m_GA_e)-AIC(m_GA_d) 
  # Hisco does not improve model fit
  
  # goitre
  m_GA_f<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+Goitre, data=pandemy_livebirths)
  AIC(m_GA_f)-AIC(m_GA_d) 
  # Goitre doesnt improve model fit
  
  # rickets
  m_GA_g<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+rickets, data=pandemy_livebirths)
  AIC(m_GA_g)-AIC(m_GA_d) 
  # Rickets doesnt improve model fit
  
 # final model
   m_GA_d<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=pandemy_livebirths)
   summary(m_GA_d)
   nobs(m_GA_d) 
   
car::vif(m_GA_d)    

plot(m_GA_d)
```

## Table
```{r}
GA_GLM_flu_mod <- round(head(estimates_cont_rlm(m_GA_d),15), 2)

  GA_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  GA_GLM_flu_mod['category'] <- c(" ",
                          "yes", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  GA_GLM_flu_mod<-GA_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_GA_gt <- GA_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,999")
    M_GA_gt
    
M_GA_gt%>%
  gtsave(here("output/tables/main_models/multivariable/rlm", "M_GA_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

## Marginally adjusted means
```{r}
m_GA_a_mmeans_multiv <- ggemmeans(m_GA_d, "Flu_in_pregn_and_in_pandemic")
m_GA_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_GA_a_mmeans_multiv) 

 m_GA_a_mmeans_multiv['outcome'] <- c("gestational age (weeks)")
   m_GA_a_mmeans_multiv['flu exp'] <- c("no", "yes")

 m_GA_a_mmeans_multiv<-m_GA_a_mmeans_multiv[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


# Birthweight 
```{r}
   m_BW<- rlm(birthweight ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+rickets+Goitre+hisco_class_3, data=pandemy_livebirths)

# Perform stepwise selection (done with glm but doesnt work for rlm)
# scope_list <- list(
#   lower = ~ Flu_in_pregn_and_in_pandemic + age_mother + height + parity_cat2 + sex + season,
#   upper = ~ Flu_in_pregn_and_in_pandemic + age_mother + height + parity_cat2 + sex + season +
#              morphology + civil_status_cat2 + Lausanne_NEU + rickets + Goitre + hisco_class_3
# )

# # Perform stepwise selection
# m_BW_d <- step(m_BW, scope = scope_list)
# summary(m_BW_d)
# plot(m_BW_d)

m_BW_d<- rlm(birthweight ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=pandemy_livebirths)
```

## Table
```{r}
BW_GLM_flu_mod <- round(head(estimates_cont_rlm(m_BW_d),15), 2)

  BW_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  BW_GLM_flu_mod['category'] <- c(" ",
                          "yes", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  BW_GLM_flu_mod<-BW_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_BW_gt <- BW_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,999")
    M_BW_gt
    
M_BW_gt%>%
  gtsave(here("output/tables/main_models/multivariable/rlm", "M_BW_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

## Marginally adjusted means
```{r}
m_BW_a_mmeans_multiv <- ggemmeans(m_BW_d, "Flu_in_pregn_and_in_pandemic")
m_BW_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_BW_a_mmeans_multiv) 

 m_BW_a_mmeans_multiv['outcome'] <- c("birth weight (g)")
    m_BW_a_mmeans_multiv['flu exp'] <- c("no", "yes")
  m_BW_a_mmeans_multiv<-m_BW_a_mmeans_multiv[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Head circumference 
```{r}
 m_HC_d <- rlm(head_circ ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=pandemy_livebirths)
```
## Table
```{r}
HC_GLM_flu_mod <- round(head(estimates_cont_rlm(m_HC_d),15), 2)

  HC_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  HC_GLM_flu_mod['category'] <- c(" ",
                          "yes", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  HC_GLM_flu_mod <- HC_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_HC_gt <- HC_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,992")
    M_HC_gt
    
M_HC_gt%>%
  gtsave(here("output/tables/main_models/multivariable/rlm", "M_HC_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

## Marginally adjusted means
```{r}
m_HC_a_mmeans_multiv <- ggemmeans(m_HC_d, "Flu_in_pregn_and_in_pandemic")
m_HC_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_HC_a_mmeans_multiv) 

 m_HC_a_mmeans_multiv['outcome'] <- c("head circumference (cm)")
 m_HC_a_mmeans_multiv['flu exp'] <- c("no", "yes")
  m_HC_a_mmeans_multiv<-m_HC_a_mmeans_multiv[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


# Placenta weight 
```{r}
m_PW_d<- rlm(placentaweight ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=pandemy_livebirths)
```

## Table
```{r}
PW_GLM_flu_mod <- round(head(estimates_cont_rlm(m_PW_d),15), 2)

PW_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  PW_GLM_flu_mod['category'] <- c(" ",
                          "yes", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  PW_GLM_flu_mod <- PW_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_PW_gt <- PW_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,977")
    M_PW_gt
    
M_PW_gt%>%
  gtsave(here("output/tables/main_models/multivariable/rlm", "M_PW_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

## Marginally adjusted means
```{r}
m_PW_a_mmeans_multiv <- ggemmeans(m_PW_d, "Flu_in_pregn_and_in_pandemic")
m_PW_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_PW_a_mmeans_multiv) 

 m_PW_a_mmeans_multiv['outcome'] <- c("placenta weight (g)")
  m_PW_a_mmeans_multiv['flu exp'] <- c("no", "yes")
  m_PW_a_mmeans_multiv<-m_PW_a_mmeans_multiv[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Birth length 
```{r}
m_BL_d<- rlm(babylength ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=pandemy_livebirths)
```

## Table
```{r}
BL_GLM_flu_mod <- round(head(estimates_cont_rlm(m_BL_d),15), 2)

  BL_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  BL_GLM_flu_mod['category'] <- c(" ",
                          "yes", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  BL_GLM_flu_mod <- BL_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_BL_gt <- BL_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,1997")
    M_BL_gt
    
M_BL_gt%>%
  gtsave(here("output/tables/main_models/multivariable/rlm", "M_BL_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

## Marginally adjusted means
```{r}
m_BL_a_mmeans_multiv <- ggemmeans(m_BL_d, "Flu_in_pregn_and_in_pandemic")
m_BL_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_BL_a_mmeans_multiv) 

 m_BL_a_mmeans_multiv['outcome'] <- c("birth length (cm)")
    m_BL_a_mmeans_multiv['flu exp'] <- c("no", "yes")
 m_BL_a_mmeans_multiv<-m_BL_a_mmeans_multiv[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


# PI 
```{r}
  m_PI_a<- rlm(PI ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season, data=pandemy_livebirths)
  summary(m_PI_a)
  
  #adding variables one at a time
  #morphology
  m_PI_b<- rlm(PI ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology, data=pandemy_livebirths)
  AIC(m_PI_b)-AIC(m_PI_a) 
  #morphology improves model fit
  
  # civil status
  m_PI_c <- rlm(PI ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2, data=pandemy_livebirths)
   AIC(m_PI_c)-AIC(m_PI_b) 
  #civil status improves model fit

   # living inside Lausanne
  m_PI_d<- rlm(PI ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=pandemy_livebirths)
  AIC(m_PI_d)-AIC(m_PI_c) 
  # Lausanne improves model fit
  
   # HISCO class
  m_PI_e<- rlm(PI ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+hisco_class_3, data=pandemy_livebirths)
  AIC(m_PI_e)-AIC(m_PI_d) 
  # Hisco does not improve model fit
  
  # goitre
  m_PI_f<- rlm(PI ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+Goitre, data=pandemy_livebirths)
  AIC(m_PI_f)-AIC(m_PI_d) 
  # Goitre doesnt improve model fit
  
  # rickets
  m_PI_g<- rlm(PI ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+rickets, data=pandemy_livebirths)
  AIC(m_PI_g)-AIC(m_PI_d) 
  # Rickets doesnt improve model fit
  
 # final model
   m_PI_d<- rlm(PI ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=pandemy_livebirths)
   summary(m_PI_d)
   nobs(m_PI_d)
```

## Table
```{r}
PI_GLM3 <- round(head(estimates_cont_rlm(m_PI_d),15), 2)

  PI_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  PI_GLM3['category'] <- c(" ",
                          "yes", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  PI_GLM3 <- PI_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PI_gt <- PI_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,997")
    M_PI_gt
    
M_PI_gt%>%
  gtsave(here("output/tables/main_models/multivariable/rlm", "M_PI_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

## Marginally adjusted means
```{r}
m_PI_a_mmeans_multiv <- ggemmeans(m_PI_d, "Flu_in_pregn_and_in_pandemic")
m_PI_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_PI_a_mmeans_multiv) 

 m_PI_a_mmeans_multiv['outcome'] <- c("ponderal index")
     m_PI_a_mmeans_multiv['flu exp'] <- c("no", "yes")
  m_PI_a_mmeans_multiv<-m_PI_a_mmeans_multiv[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Pooling the tables for predicted means together
```{r}
a_m_cont_outc_u_multiv <- rbind(m_BW_a_mmeans_multiv, m_HC_a_mmeans_multiv,
                                m_PW_a_mmeans_multiv,m_BL_a_mmeans_multiv,
                                m_PI_a_mmeans_multiv, m_GA_a_mmeans_multiv)
a_m_cont_outc_u_multiv <- a_m_cont_outc_u_multiv %>%
  mutate(sex="all",
         model="multivariable")
a_m_cont_outc_u_multiv%>%
  gt() %>%
  gtsave(here("output/tables/main_models/multivariable/rlm", "M_cont_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```



# LBW 
```{r}
 m_LBW_a<- glm(LBW ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season, family = "binomial", data=pandemy_livebirths)
  summary(m_LBW_a)

  #adding variables one at a time
  #morphology
  m_LBW_b<- glm(LBW ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology, family = "binomial", data=pandemy_livebirths)
  AIC(m_LBW_b)-AIC(m_LBW_a) 
  #morphology improves model fit
  
  # civil status
  m_LBW_c <- glm(LBW ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2, family = "binomial", data=pandemy_livebirths)
   AIC(m_LBW_c)-AIC(m_LBW_b) 
  #civil status improves model fit

   # living inside Lausanne
  m_LBW_d<- glm(LBW ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, family = "binomial", data=pandemy_livebirths)
  AIC(m_LBW_d)-AIC(m_LBW_c) 
  # Lausanne improves model fit
  
   # HISCO class
  m_LBW_e<- glm(LBW ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+hisco_class_3, family = "binomial", data=pandemy_livebirths)
  AIC(m_LBW_e)-AIC(m_LBW_d) 
  # Hisco does not improve model fit
  
  # goitre
  m_LBW_f<- glm(LBW ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+Goitre, family = "binomial", data=pandemy_livebirths)
  AIC(m_LBW_f)-AIC(m_LBW_d) 
  # Goitre does improve model fit but not kept for consistency among models
  
  # rickets
  m_LBW_g<- glm(LBW ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+rickets, family = "binomial", data=pandemy_livebirths)
  AIC(m_LBW_g)-AIC(m_LBW_d) 
  # Rickets doesnt improve model fit
  
 # final model
   m_LBW_d<- glm(LBW ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, family = "binomial", data=pandemy_livebirths)
   summary(m_LBW_d)
   nobs(m_LBW_d)  
   car::vif(m_LBW_d)

```

## Table
```{r}
LBW_GLM3 <- round(head(estimates_binary(m_LBW_d),15), 2)

  LBW_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  LBW_GLM3['category'] <- c(" ",
                          "yes", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  LBW_GLM3<-LBW_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_LBW_gt <- LBW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,999")
    M_LBW_gt
    
LBW_estimates_gt <- M_LBW_gt%>%
  gtsave(here("output/tables/main_models/multivariable", "M_LBW_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

## Marginal proportions
```{r}
m_LBW_a_mmeans_multiv <- ggemmeans(m_LBW_d, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
m_LBW_a_mmeans_multiv <- mmeans_ci_vertic_bin(m_LBW_a_mmeans_multiv) 

 m_LBW_a_mmeans_multiv['outcome'] <- c("LBW (<2,500g)")
    m_LBW_a_mmeans_multiv['flu exp'] <- c("no", "yes")
 m_LBW_a_mmeans_multiv<-m_LBW_a_mmeans_multiv[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
m_LBW_a_mmeans_multiv
```

# PTB 
```{r}
 m_PTB_a<- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season, family = "binomial", data=pandemy_livebirths)
  summary(m_PTB_a)

#adding variables one at a time
  #morphology
  m_PTB_b<- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology, family = "binomial", data=pandemy_livebirths)
  AIC(m_PTB_b)-AIC(m_PTB_a) 
  #morphology improves model fit
  
  # civil status
  m_PTB_c <- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2, family = "binomial", data=pandemy_livebirths)
   AIC(m_PTB_c)-AIC(m_PTB_b) 
  #civil status improves model fit

   # living inside Lausanne
  m_PTB_d<- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, family = "binomial", data=pandemy_livebirths)
  AIC(m_PTB_d)-AIC(m_PTB_c) 
  # Lausanne improves model fit
  
   # HISCO class
  m_PTB_e<- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+hisco_class_3, family = "binomial", data=pandemy_livebirths)
  AIC(m_PTB_e)-AIC(m_PTB_d) 
  # Hisco does not improve model fit
  
  # goitre
  m_PTB_f<- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+Goitre, family = "binomial", data=pandemy_livebirths)
  AIC(m_PTB_f)-AIC(m_PTB_d) 
  # Goitre doesnt improve model fit
  
  # rickets
  m_PTB_g<- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU+rickets, family = "binomial", data=pandemy_livebirths)
  AIC(m_PTB_g)-AIC(m_PTB_d) 
  # Rickets doesnt improve model fit
  
 # final model
   m_PTB_d<- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, family = "binomial", data=pandemy_livebirths)
   summary(m_PTB_d)
   nobs(m_PTB_d)  
   car::vif(m_PTB_d)
```

## Table
```{r}
PTB_GLM3 <- round(head(estimates_binary(m_PTB_d),15), 2)

  PTB_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  PTB_GLM3['category'] <- c(" ",
                          "yes", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  PTB_GLM3<-PTB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_PTB_gt <- PTB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,999")
    M_PTB_gt
    
PTB_estimates_gt <- M_PTB_gt%>%
  gtsave(here("output/tables/main_models/multivariable", "M_PTB_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

## Marginal proportions
```{r}
m_PTB_a_mmeans_multiv <- ggemmeans(m_PTB_d, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
m_PTB_a_mmeans_multiv <- mmeans_ci_vertic_bin(m_PTB_a_mmeans_multiv) 

 m_PTB_a_mmeans_multiv['outcome'] <- c("PTB (<37 weeks)")
 m_PTB_a_mmeans_multiv['flu exp'] <- c("no", "yes")
m_PTB_a_mmeans_multiv<-m_PTB_a_mmeans_multiv[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
m_PTB_a_mmeans_multiv
```


# Pooling the tables for marginal proportions
```{r}
a_m_bin_outc_multiv <- rbind(m_LBW_a_mmeans_multiv, m_PTB_a_mmeans_multiv)
a_m_bin_outc_multiv <- a_m_bin_outc_multiv %>%
  mutate(sex="all",
         model="multivariable")

a_m_bin_outc_multiv%>%
  gt() %>%
  gtsave(here("output/tables/main_models/multivariable", "M_bin_marg_prop_Flu_in_pregn_and_in_pandemic_gt.docx"))
```


