---
title: "Univariable models"
author: "Mathilde Le Vu"
date: "2024-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exclusions
Between 1905 and 1924, there are `r dim(laus1.1)[1]` births included in our database.

From this, we successively excluded:

- Home births n= `r sum(laus1.1$Homebirth2 == "yes")`,
`r round(100 * (sum(!is.na(laus1.1$Homebirth2) & laus1.1$Homebirth2 == "yes") / sum(!is.na(laus1.1$Homebirth2))), digits = 2)[1]` %. New Number of cases: `r dim(laus1.2)[1]`

- Gestational age (based on variables GA_weeks) <22 (to fit today definitions of stillbirth), or birthweight <500g. 
n= `r (dim(laus1.2)-dim(laus1.3))[1]`, `r round(100 * (dim(laus1.2) -dim(laus1.3))/dim(laus1.2), digits = 2)[1]`.
New Number of cases: `r dim(laus1.3)[1]`

- "Extreme outliers" for birthweight and head circumference based on Z-scores adjusted for sex. I have chosen the threshold of 7 Z score. We then excluded
n= `r (dim(laus1.3)-dim(laus2))[1]`, `r round(100 * (dim(laus1.3) -dim(laus2))/dim(laus1.3), digits = 2)[1]`.
New Number of cases: `r dim(laus2)[1]`

## Gestational age 
```{r}
  m_GA_u<- rlm(GA_weeks_corrected ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths)
  summary(m_GA_u)
  nobs(m_GA_u)
```

### Table
```{r}
GA_GLM_flu_mod <- round(head(estimates_cont_rlm(m_GA_u)), 2)
# GA_GLMmod <- GA_GLM_flu_mod %>%
# mutate(pvalue=as.numeric(pvalue)) %>%
# mutate(pvalue1=pvalue) 
# GA_GLMmod$pvalue <-  format(round(GA_GLMmod$pvalue, digits=2), nsmall=2)
# GA_GLMmod <- GA_GLMmod%>% 
#     mutate(pvalue1=case_when((pvalue1<0.0001)~ "<0.0001",
#                              (pvalue1<0.001)~ "<0.001")) 
# GA_GLMmod$pvalue1 <- (ifelse(is.na(GA_GLMmod$pvalue1), GA_GLMmod$pvalue,  GA_GLMmod$pvalue1))
# GA_GLMmod <- GA_GLMmod %>%
#   select(-one_of('pvalue'))  
# GA_GLM3 <- GA_GLMmod %>%
# rename(pvalue=pvalue1) %>%
#     mutate_if(is.numeric, ~ format(round(., digits = 2), nsmall = 2))

  GA_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  GA_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  GA_GLM_flu_mod<-GA_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_GA_gt <- GA_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,085")
   M_GA_gt

M_GA_gt%>%
  gtsave(here("output/tables/main_models/univariable/rlm", "M_GA_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

### Marginally adjusted means
```{r}
m_GA_a_mmeans <- ggemmeans(m_GA_u, "Flu_in_pregn_and_in_pandemic")
m_GA_a_mmeans <- mmeans_ci_vertic_cont(m_GA_a_mmeans) 


 m_GA_a_mmeans['outcome'] <- c("gestational age (weeks)")
  m_GA_a_mmeans['flu exp'] <- c("no", "yes")
   m_GA_a_mmeans<-m_GA_a_mmeans[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

## Birthweight 
```{r}
  m_BW_u<- rlm(birthweight ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths)
  summary(m_BW_u)
  nobs(m_BW_u)
```

### Table
```{r}
BW_GLM_flu_mod <- round(head(estimates_cont_rlm(m_BW_u)), 2)

  BW_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  BW_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  BW_GLM_flu_mod<-BW_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_BW_gt <- BW_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,085")
    M_BW_gt

M_BW_gt%>%
  gtsave(here("output/tables/main_models/univariable/rlm", "M_BW_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

### Marginally adjusted means
```{r}
m_BW_a_mmeans <- ggemmeans(m_BW_u, "Flu_in_pregn_and_in_pandemic")
m_BW_a_mmeans <- mmeans_ci_vertic_cont(m_BW_a_mmeans) 

 m_BW_a_mmeans['outcome'] <- c("birth weight (g)")
    m_BW_a_mmeans['flu exp'] <- c("no", "yes")
 m_BW_a_mmeans<-m_BW_a_mmeans[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

## Head circumference 
```{r}
  m_HC_u<- rlm(head_circ ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths)
summary(m_HC_u)
nobs(m_HC_u)
```
### Table
```{r}
HC_GLM_flu_mod <- round(head(estimates_cont_rlm(m_HC_u)), 2)

  HC_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  HC_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  HC_GLM_flu_mod <- HC_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_HC_gt <- HC_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,077")
    M_HC_gt
    
M_HC_gt%>%
  gtsave(here("output/tables/main_models/univariable/rlm", "M_HC_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```


### Marginally adjusted means
```{r}
m_HC_a_mmeans <- ggemmeans(m_HC_u, "Flu_in_pregn_and_in_pandemic")
m_HC_a_mmeans <- mmeans_ci_vertic_cont(m_HC_a_mmeans) 

 m_HC_a_mmeans['outcome'] <- c("head circumference (cm)")
  m_HC_a_mmeans['flu exp'] <- c("no", "yes")
 m_HC_a_mmeans<-m_HC_a_mmeans[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

## Placenta weight 
```{r}
  m_PW_u<- rlm(placentaweight ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths)
  summary(m_PW_u)
  nobs(m_PW_u)
```

### Table
```{r}
PW_GLM_flu_mod <- round(head(estimates_cont_rlm(m_PW_u)), 2)

  PW_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  PW_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  PW_GLM_flu_mod <- PW_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_PW_gt <- PW_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,059")
    M_PW_gt
    
M_PW_gt%>%
  gtsave(here("output/tables/main_models/univariable/rlm", "M_PW_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

### Marginally adjusted means
```{r}
m_PW_a_mmeans <- ggemmeans(m_PW_u, "Flu_in_pregn_and_in_pandemic")
m_PW_a_mmeans <- mmeans_ci_vertic_cont(m_PW_a_mmeans) 

 m_PW_a_mmeans['outcome'] <- c("placenta weight (g)")
   m_PW_a_mmeans['flu exp'] <- c("no", "yes")
  m_PW_a_mmeans<-m_PW_a_mmeans[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


## Birth length 
```{r}
  m_BL_u<- rlm(babylength ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths)
  summary(m_BL_u)
  nobs(m_BL_u)
```
### Table
```{r}
BL_GLM_flu_mod <- round(head(estimates_cont_rlm(m_BL_u)), 2)


  BL_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  BL_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  BL_GLM_flu_mod <- BL_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_BL_gt <- BL_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,081")
    M_BL_gt
    
M_BL_gt%>%
  gtsave(here("output/tables/main_models/univariable/rlm", "M_BL_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

### Marginally adjusted means
```{r}
m_BL_a_mmeans <- ggemmeans(m_BL_u, "Flu_in_pregn_and_in_pandemic")
m_BL_a_mmeans <- mmeans_ci_vertic_cont(m_BL_a_mmeans) 

 m_BL_a_mmeans['outcome'] <- c("birth length (cm)")
   m_BL_a_mmeans['flu exp'] <- c("no", "yes")
   m_BL_a_mmeans<-m_BL_a_mmeans[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


## PI 
```{r}
  m_PI_u<- rlm(PI ~ Flu_in_pregn_and_in_pandemic, data=pandemy_livebirths)
  summary(m_PI_u)
  nobs(m_PI_u)
```

### Table
```{r}
PI_GLM_flu_mod <- round(head(estimates_cont_rlm(m_PI_u)), 2)

  PI_GLM_flu_mod['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  PI_GLM_flu_mod['category'] <- c(" ",
                          "yes")
  PI_GLM_flu_mod <- PI_GLM_flu_mod[, c('Parameters', "category", "beta", "lci","uci")]

   M_PI_gt <- PI_GLM_flu_mod %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,081")
    M_PI_gt
    
M_PI_gt%>%
  gtsave(here("output/tables/main_models/univariable/rlm", "M_PI_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

### Marginally adjusted means
```{r}
m_PI_a_mmeans <- ggemmeans(m_PI_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
m_PI_a_mmeans <- mmeans_ci_vertic_cont(m_PI_a_mmeans) 

 m_PI_a_mmeans['outcome'] <- c("ponderal index")
    m_PI_a_mmeans['flu exp'] <- c("no", "yes")
  m_PI_a_mmeans<-m_PI_a_mmeans[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Pooling the tables for predicted means together
```{r}
a_m_cont_outc_u <- rbind(m_BW_a_mmeans, m_HC_a_mmeans,
                         m_PW_a_mmeans, m_BL_a_mmeans,
                         m_PI_a_mmeans,m_GA_a_mmeans)
a_m_cont_outc_u <- a_m_cont_outc_u %>%
  mutate(mean=round(mean, 2),
         lci=round(lci, 2),
         uci=round(uci, 2),
         sex="all",
         model="univariable")
a_m_cont_outc_u%>%
  gt() %>%
  gtsave(here("output/tables/main_models/univariable/rlm", "M_cont_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```


# GLM: binary outcomes 

## LBW 
```{r}
 m_LBW_u<- glm(LBW ~ Flu_in_pregn_and_in_pandemic, family = "binomial", data=pandemy_livebirths)
  summary(m_LBW_u)
  nobs(m_LBW_u)
```

### Table
```{r}
LBW_GLM3 <- round(head(estimates_binary(m_LBW_u)), 2)

  LBW_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  LBW_GLM3['category'] <- c(" ",
                          "yes")
  LBW_GLM3<-LBW_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_LBW_gt <- LBW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,085")
    M_LBW_gt
    
LBW_estimates_gt <- M_LBW_gt%>%
  gtsave(here("output/tables/main_models/univariable", "M_LBW_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

### Marginal proportions
```{r}
m_LBW_a_mmeans_u <- ggemmeans(m_LBW_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
m_LBW_a_mmeans_u <- mmeans_ci_vertic_bin(m_LBW_a_mmeans_u) 

 m_LBW_a_mmeans_u['outcome'] <- c("LBW (<2,500g)")
 m_LBW_a_mmeans_u['flu exp'] <- c("no", "yes")
  m_LBW_a_mmeans_u<-m_LBW_a_mmeans_u[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


## stillbirth 
```{r}
 m_SB_u<- glm(stillbirth ~ Flu_in_pregn_and_in_pandemic, family = binomial, data=pandemy)
  summary(m_SB_u)
  nobs(m_SB_u)
```

### Table
```{r}
SB_GLM3 <- round(head(estimates_binary(m_SB_u)), 2)

  SB_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  SB_GLM3['category'] <- c(" ",
                          "yes")
  SB_GLM3<-SB_GLM3[, c('Parameters', "category", "OR", "lci","uci", "pvalue")]

   M_SB_gt <- SB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,177")
    M_SB_gt
    
SB_estimates_gt <- M_SB_gt%>%
  gtsave(here("output/tables/main_models/univariable", "M_SB_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

### Marginal proportions
```{r}
m_SB_a_mmeans_u <- ggemmeans(m_SB_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
m_SB_a_mmeans_u <- mmeans_ci_vertic_bin(m_SB_a_mmeans_u) 

 m_SB_a_mmeans_u['outcome'] <- c("stillbirth")
  m_SB_a_mmeans_u['flu exp'] <- c("no", "yes")

  m_SB_a_mmeans_u<-m_SB_a_mmeans_u[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

## PTB 
```{r}
 m_PTB_u<- glm(PTB_corrected ~ Flu_in_pregn_and_in_pandemic, family = "binomial", data=pandemy_livebirths)
  summary(m_PTB_u)
  nobs(m_PTB_u)
```
### Table
```{r}
PTB_GLM3 <- round(head(estimates_binary(m_PTB_u)), 2)

  PTB_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  PTB_GLM3['category'] <- c(" ",
                          "yes")
  PTB_GLM3<-PTB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_PTB_gt <- PTB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,085")
    M_PTB_gt
    
PTB_estimates_gt <- M_PTB_gt%>%
  gtsave(here("output/tables/main_models/univariable", "M_PTB_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

### Marginal proportions
```{r}
m_PTB_a_mmeans_u <- ggemmeans(m_PTB_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
m_PTB_a_mmeans_u <- mmeans_ci_vertic_bin(m_PTB_a_mmeans_u) 

 m_PTB_a_mmeans_u['outcome'] <- c("PTB (<37 weeks)")
  m_PTB_a_mmeans_u['flu exp'] <- c("no", "yes")

  m_PTB_a_mmeans_u<-m_PTB_a_mmeans_u[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


## Neonat mortality
```{r}
 m_NM_u<- glm(neonat_mort_d1_d5 ~ Flu_in_pregn_and_in_pandemic, family = "binomial", data=pandemy_livebirths)
  summary(m_NM_u)
  nobs(m_NM_u)
```

### Table
```{r}
NM_GLM3 <- round(head(estimates_binary(m_NM_u)), 2)

  NM_GLM3['Parameters'] <- c("intercept", 
                            "Flu during pregnancy (ref: no)"
                            )
  NM_GLM3['category'] <- c(" ",
                          "yes")
  NM_GLM3<-NM_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_NM_gt <- NM_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  )%>%
     tab_source_note(source_note = "n=2,084")
    M_NM_gt
    
NM_estimates_gt <- M_NM_gt%>%
  gtsave(here("output/tables/main_models/univariable", "M_NM_estimates_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

### Marginal proportions
```{r}
m_NM_a_mmeans_u <- ggemmeans(m_NM_u, "Flu_in_pregn_and_in_pandemic", margin="marginalmeans")
m_NM_a_mmeans_u <- mmeans_ci_vertic_bin(m_NM_a_mmeans_u) 

 m_NM_a_mmeans_u['outcome'] <- c("early neonatal mortality")
  m_NM_a_mmeans_u['flu exp'] <- c("no", "yes")
 m_NM_a_mmeans_u<-m_NM_a_mmeans_u[, c("outcome",'flu exp', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


# Pooling the tables for marginal proportions
```{r}
a_m_bin_outc_u <- rbind(m_LBW_a_mmeans_u,m_PTB_a_mmeans_u,
                        m_SB_a_mmeans_u,m_NM_a_mmeans_u)
a_m_bin_outc_u <- a_m_bin_outc_u %>%
  mutate(sex="all",
         model="univariable")
a_m_bin_outc_u%>%
  gt() %>%
  gtsave(here("output/tables/main_models/univariable", "M_bin_marg_prop_Flu_in_pregn_and_in_pandemic_gt.docx"))
```


