---
title: "Univariable models"
author: "Mathilde Le Vu"
date: "2024-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Gestational age 
```{r}
  m_GA_multiv_sev<- rlm(GA_weeks_corrected ~ Grippe_severity3+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=flu_cases_during_pregn_pandemy_sev_livebirths)
   summary(m_GA_multiv_sev)
   nobs(m_GA_multiv_sev)
```

## Table
```{r}
GA_GLM3 <- round(head(estimates_cont_rlm(m_GA_multiv_sev),16), 2)

  GA_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", "","Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  GA_GLM3['category'] <- c(" ",
                          "mild", "severe", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  GA_GLM3<-GA_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_GA_gt <- GA_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,958")
    M_GA_gt
    
M_GA_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/severity/multivariable/rlm", "M_GA_severity_multiv.docx"))
```
## Marginally adjusted means
```{r}
m_GA_a_mmeans_multiv <- ggemmeans(m_GA_multiv_sev, "Grippe_severity3")
m_GA_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_GA_a_mmeans_multiv) 

 m_GA_a_mmeans_multiv['outcome'] <- c("gestational age (weeks)")
   m_GA_a_mmeans_multiv['severity'] <- c("no", "mild", "severe")

 m_GA_a_mmeans_multiv<-m_GA_a_mmeans_multiv[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Birthweight 
```{r}
  m_BW_multiv_sev<- rlm(birthweight ~ Grippe_severity3+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=flu_cases_during_pregn_pandemy_sev_livebirths)
   summary(m_BW_multiv_sev)
   nobs(m_BW_multiv_sev)
```

### Table
```{r}
BW_GLM3 <- round(head(estimates_cont_rlm(m_BW_multiv_sev),16), 2)

  BW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", "","Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  BW_GLM3['category'] <- c(" ",
                          "mild", "severe", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  BW_GLM3<-BW_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_BW_gt <- BW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,958")
    M_BW_gt
    
M_BW_gt%>%
    gtsave(here("output/tables/models_flu_trimester_or_severity/severity/multivariable/rlm", "M_BW_severity_multiv.docx"))
```

## Marginally adjusted means
```{r}
m_BW_a_mmeans_multiv <- ggemmeans(m_BW_multiv_sev, "Grippe_severity3")
m_BW_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_BW_a_mmeans_multiv) 

 m_BW_a_mmeans_multiv['outcome'] <- c("birth weight (g)")
  m_BW_a_mmeans_multiv['severity'] <- c("no", "mild", "severe")
  m_BW_a_mmeans_multiv<-m_BW_a_mmeans_multiv[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Head circumference 
```{r}
   m_HC_multiv_sev<- rlm(head_circ ~ Grippe_severity3+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=flu_cases_during_pregn_pandemy_sev_livebirths)
   summary(m_HC_multiv_sev)
   nobs(m_HC_multiv_sev)
```

## Table
```{r}
HC_GLM3 <- round(head(estimates_cont_rlm(m_HC_multiv_sev),16), 2)

  HC_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", "",  "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  HC_GLM3['category'] <- c(" ",
                          "mild", "severe", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  HC_GLM3 <- HC_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_HC_gt <- HC_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,951")
    M_HC_gt
    
M_HC_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/severity/multivariable/rlm", "M_HC_severity_multiv.docx"))
```

## Marginally adjusted means
```{r}
m_HC_a_mmeans_multiv <- ggemmeans(m_HC_multiv_sev, "Grippe_severity3")
m_HC_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_HC_a_mmeans_multiv) 

 m_HC_a_mmeans_multiv['outcome'] <- c("head circumference (cm)")
 m_HC_a_mmeans_multiv['severity'] <- c("no", "mild", "severe")
  m_HC_a_mmeans_multiv<-m_HC_a_mmeans_multiv[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Placenta weight 
```{r}
 m_PW_multiv_sev<- rlm(placentaweight ~ Grippe_severity3+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=flu_cases_during_pregn_pandemy_sev_livebirths)
   summary(m_PW_multiv_sev)
   nobs(m_PW_multiv_sev)
```

## Table
```{r}
PW_GLM3 <- round(head(estimates_cont_rlm(m_PW_multiv_sev),16), 2)

  PW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", "", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  PW_GLM3['category'] <- c(" ",
                          "mild", "severe", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  PW_GLM3 <- PW_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PW_gt <- PW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,936")
    M_PW_gt
    
M_PW_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/severity/multivariable/rlm", "M_PW_severity_multiv.docx"))
```

## Marginally adjusted means
```{r}
m_PW_a_mmeans_multiv <- ggemmeans(m_PW_multiv_sev, "Grippe_severity3")
m_PW_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_PW_a_mmeans_multiv) 

 m_PW_a_mmeans_multiv['outcome'] <- c("placenta weight (g)")
  m_PW_a_mmeans_multiv['severity'] <- c("no", "mild", "severe")
  m_PW_a_mmeans_multiv<-m_PW_a_mmeans_multiv[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Birth length 
```{r}
  m_BL_multiv_sev<- rlm(babylength ~ Grippe_severity3+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=flu_cases_during_pregn_pandemy_sev_livebirths)
   summary(m_BL_multiv_sev)
   nobs(m_BL_multiv_sev)
```

## Table
```{r}
BL_GLM3 <- round(head(estimates_cont_rlm(m_BL_multiv_sev),16), 2)

  BL_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", "", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  BL_GLM3['category'] <- c(" ",
                          "mild", "severe", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  BL_GLM3 <- BL_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_BL_gt <- BL_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,956")
    M_BL_gt
    
M_BL_gt%>%
    gtsave(here("output/tables/models_flu_trimester_or_severity/severity/multivariable/rlm", "M_BL_severity_multiv.docx"))
```

## Marginally adjusted means
```{r}
m_BL_a_mmeans_multiv <- ggemmeans(m_BL_multiv_sev, "Grippe_severity3")
m_BL_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_BL_a_mmeans_multiv) 

 m_BL_a_mmeans_multiv['outcome'] <- c("birth length (cm)")
    m_BL_a_mmeans_multiv['severity'] <- c("no", "mild", "severe")
 m_BL_a_mmeans_multiv<-m_BL_a_mmeans_multiv[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

## PI 
```{r}
  m_PI_multiv_sev<- rlm(PI ~ Grippe_severity3+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, data=flu_cases_during_pregn_pandemy_sev_livebirths)
   summary(m_PI_multiv_sev)
   nobs(m_PI_multiv_sev)
```

## Table
```{r}
PI_GLM3 <- round(head(estimates_cont_rlm(m_PI_multiv_sev),16), 2)

  PI_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", "",  "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  PI_GLM3['category'] <- c(" ",
                          "mild", "severe", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  PI_GLM3 <- PI_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PI_gt <- PI_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,956")
    M_PI_gt
    
M_PI_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/severity/multivariable/rlm", "M_PI_severity_multiv.docx"))
```

## Marginally adjusted means
```{r}
m_PI_a_mmeans_multiv <- ggemmeans(m_PI_multiv_sev, "Grippe_severity3")
m_PI_a_mmeans_multiv <- mmeans_ci_vertic_cont(m_PI_a_mmeans_multiv) 

 m_PI_a_mmeans_multiv['outcome'] <- c("ponderal index")
     m_PI_a_mmeans_multiv['severity'] <- c("no", "mild", "severe")
  m_PI_a_mmeans_multiv<-m_PI_a_mmeans_multiv[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Pooling the tables for predicted means together
```{r}
a_m_cont_outc_u_multiv_sev <- rbind(m_BW_a_mmeans_multiv,m_HC_a_mmeans_multiv,
                                m_PW_a_mmeans_multiv, m_BL_a_mmeans_multiv,
                                m_PI_a_mmeans_multiv, m_GA_a_mmeans_multiv)
a_m_cont_outc_u_multiv_sev <- a_m_cont_outc_u_multiv_sev %>%
  mutate(sex="all",
         model="multivariable")
a_m_cont_outc_u_multiv_sev%>%
  gt() %>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/severity/multivariable/rlm", "M_cont_estimates_Flu_severity_multiv_rlm_gt.docx"))
```


# LBW 
```{r}
  m_LBW_multiv_sev<- glm(LBW ~ Grippe_severity3+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths)
   summary(m_LBW_multiv_sev)
   nobs(m_LBW_multiv_sev)  
```

## Table
```{r}
LBW_GLM3 <- round(head(estimates_binary(m_LBW_multiv_sev),16), 2)

  LBW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", "",  "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  LBW_GLM3['category'] <- c(" ",
                          "mild", "severe", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  LBW_GLM3<-LBW_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_LBW_gt <- LBW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,958")
    M_LBW_gt
    
LBW_estimates_gt <- M_LBW_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/severity/multivariable","M_LBW_severity_multiv.docx"))
```

## Marginal proportions
```{r}
m_LBW_a_mmeans_multiv <- ggemmeans(m_LBW_multiv_sev, "Grippe_severity3", margin="marginalmeans")
m_LBW_a_mmeans_multiv <- mmeans_ci_vertic_bin(m_LBW_a_mmeans_multiv) 

 m_LBW_a_mmeans_multiv['outcome'] <- c("LBW (<2,500g)")
    m_LBW_a_mmeans_multiv['severity'] <- c("no", "mild", "severe")
 m_LBW_a_mmeans_multiv<-m_LBW_a_mmeans_multiv[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
m_LBW_a_mmeans_multiv
```

# PTB 
```{r}
    m_PTB_multiv_sev<- glm(PTB_corrected ~ Grippe_severity3+age_mother+height+parity_cat2+sex+
                 season+morphology+civil_status_cat2+Lausanne_NEU, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths)
   summary(m_PTB_multiv_sev)
   nobs(m_PTB_multiv_sev)  
```

## Table
```{r}
PTB_GLM3 <- round(head(estimates_binary(m_PTB_multiv_sev),16), 2)

  PTB_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", "", "Maternal age", "Maternal height",
                            "Parity (ref: 1)", "", "Sex (ref: male)", "Season (ref: spring)",
                            "", "", "Morphology (ref: none)", "", "Civil status (ref: married)",
                            "Living inside Lausanne (ref: yes)"
                            )
  PTB_GLM3['category'] <- c(" ",
                          "mild", "severe", "", "",
                          "2", ">2", "female", "summer", "autumn", "winter",
                          "obese", "thin", "single or missing", "no or unsure")
  PTB_GLM3<-PTB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_PTB_gt <- PTB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=1,958")
    M_PTB_gt
    
PTB_estimates_gt <- M_PTB_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/severity/multivariable", "M_PTB_severity_multiv.docx"))
```

## Marginal proportions
```{r}
m_PTB_a_mmeans_multiv <- ggemmeans(m_PTB_multiv_sev, "Grippe_severity3", margin="marginalmeans")
m_PTB_a_mmeans_multiv <- mmeans_ci_vertic_bin(m_PTB_a_mmeans_multiv) 

 m_PTB_a_mmeans_multiv['outcome'] <- c("PTB (<37 weeks)")
 m_PTB_a_mmeans_multiv['severity'] <- c("no", "mild", "severe")
m_PTB_a_mmeans_multiv<-m_PTB_a_mmeans_multiv[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
m_PTB_a_mmeans_multiv
```


# Pooling the tables for marginal proportions
```{r}
a_m_bin_outc_multiv_sev <- rbind(m_LBW_a_mmeans_multiv, m_PTB_a_mmeans_multiv)
a_m_bin_outc_multiv_sev <- a_m_bin_outc_multiv_sev %>%
  mutate(sex="all",
         model="multivariable")

a_m_bin_outc_multiv_sev%>%
  gt() %>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/severity/multivariable", "M_bin_marg_prop_Flu_in_pregn_and_in_pandemic_gt.docx"))
```


