---
title: "Univariable models"
author: "Mathilde Le Vu"
date: "2024-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Gest age 
```{r}
  m_GA_u_t<- rlm(GA_weeks_corrected ~ trimester_real_def3, data=flu_cases_during_pregn_pandemy_trimester_livebirths)
  summary(m_GA_u_t)
  nobs(m_GA_u_t)
```

### Table
```{r}
GA_GLM3 <- round(head(estimates_cont_rlm(m_GA_u_t)), 2)
  GA_GLM3['Parameters'] <- c("intercept", 
                            "Flu trimester (ref: no flu)", "", ""
                            )
  GA_GLM3['category'] <- c(" ",
                          "first", "second", "third")
  GA_GLM3<-GA_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_GA_gt <- GA_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,071")
    M_GA_gt
    
M_GA_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable/rlm", "M_GA_trimester_univ.docx"))
```

## Marginally adjusted means
```{r}
m_GA_a_mmeans_univ_t <- ggemmeans(m_GA_u_t, "trimester_real_def3")
m_GA_a_mmeans_univ_t <- mmeans_ci_vertic_cont(m_GA_a_mmeans_univ_t) 

 m_GA_a_mmeans_univ_t['outcome'] <- c("gestational age (weeks)")
  m_GA_a_mmeans_univ_t['trimester'] <- c("no", "first", "second", "third")

 m_GA_a_mmeans_univ_t<-m_GA_a_mmeans_univ_t[, c("outcome",'trimester', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Birthweight 
```{r}
  m_BW_u_t<- rlm(birthweight ~ trimester_real_def3, data=flu_cases_during_pregn_pandemy_trimester_livebirths)
  summary(m_BW_u_t)
  nobs(m_BW_u_t)
```

### Table
```{r}
BW_GLM3 <- round(head(estimates_cont_rlm(m_BW_u_t)), 2)

  BW_GLM3['Parameters'] <- c("intercept", 
                            "Flu trimester (ref: no flu)", "", ""
                            )
  BW_GLM3['category'] <- c(" ",
                          "first", "second", "third")
  BW_GLM3<-BW_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_BW_gt <- BW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,071")
    M_BW_gt
    
M_BW_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable/rlm", "M_BW_trimester_univ.docx"))
```

## Marginally adjusted means
```{r}
m_BW_a_mmeans_univ_t <- ggemmeans(m_BW_u_t, "trimester_real_def3")
m_BW_a_mmeans_univ_t <- mmeans_ci_vertic_cont(m_BW_a_mmeans_univ_t) 

 m_BW_a_mmeans_univ_t['outcome'] <- c("birth weight (g)")
  m_BW_a_mmeans_univ_t['trimester'] <- c("no", "first", "second", "third")

 m_BW_a_mmeans_univ_t<-m_BW_a_mmeans_univ_t[, c("outcome",'trimester', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Head circumference 
```{r}
  m_HC_u_t<- rlm(head_circ ~ trimester_real_def3, data=flu_cases_during_pregn_pandemy_trimester_livebirths)
summary(m_HC_u_t)
nobs(m_HC_u_t)
```
### Table
```{r}
HC_GLM3 <- round(head(estimates_cont_rlm(m_HC_u_t)), 2)

  HC_GLM3['Parameters'] <- c("intercept", 
                            "Flu trimester (ref: no flu)", "", ""
                            )
  HC_GLM3['category'] <- c(" ",
                          "first", "second", "third")
  HC_GLM3 <- HC_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_HC_gt <- HC_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,063")
    M_HC_gt
    
M_HC_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable/rlm", "M_HC_trimester_univ.docx"))
```

## Marginally adjusted means
```{r}
m_HC_a_mmeans_univ_t <- ggemmeans(m_HC_u_t, "trimester_real_def3")
m_HC_a_mmeans_univ_t <- mmeans_ci_vertic_cont(m_HC_a_mmeans_univ_t) 

 m_HC_a_mmeans_univ_t['outcome'] <- c("head circumference (cm)")
  m_HC_a_mmeans_univ_t['trimester'] <- c("no", "first", "second", "third")

 m_HC_a_mmeans_univ_t<-m_HC_a_mmeans_univ_t[, c("outcome",'trimester', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Placenta weight 
```{r}
  m_PW_u_t<- rlm(placentaweight ~ trimester_real_def3, data=flu_cases_during_pregn_pandemy_trimester_livebirths)
  summary(m_PW_u_t)
  nobs(m_PW_u_t)
```

### Table
```{r}
PW_GLM3 <-  round(head(estimates_cont_rlm(m_PW_u_t),17), 2)

  PW_GLM3['Parameters'] <- c("intercept", 
                            "Flu trimester (ref: no flu)", "", ""
                            )
  PW_GLM3['category'] <- c(" ",
                          "first", "second", "third")
  PW_GLM3 <- PW_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PW_gt <- PW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,045")
    M_PW_gt
    
M_PW_gt%>%
    gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable/rlm","M_PW_trimester_univ.docx"))
```
## Marginally adjusted means
```{r}
m_PW_a_mmeans_univ_t <- ggemmeans(m_PW_u_t, "trimester_real_def3")
m_PW_a_mmeans_univ_t <- mmeans_ci_vertic_cont(m_PW_a_mmeans_univ_t) 

 m_PW_a_mmeans_univ_t['outcome'] <- c("placenta weight (g)")
  m_PW_a_mmeans_univ_t['trimester'] <- c("no", "first", "second", "third")

 m_PW_a_mmeans_univ_t<-m_PW_a_mmeans_univ_t[, c("outcome",'trimester', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Birth length 
```{r}
  m_BL_u_t<- rlm(babylength ~ trimester_real_def3, data=flu_cases_during_pregn_pandemy_trimester_livebirths)
  summary(m_BL_u_t)
  nobs(m_BL_u_t)
```
### Table
```{r}
BL_GLM3 <- round(head(estimates_cont_rlm(m_BL_u_t)), 2)

  BL_GLM3['Parameters'] <- c("intercept", 
                            "Flu trimester (ref: no flu)", "", ""
                            )
  BL_GLM3['category'] <- c(" ",
                          "first", "second", "third")
  BL_GLM3 <- BL_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_BL_gt <- BL_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,067")
    M_BL_gt
    
M_BL_gt%>%
    gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable/rlm","M_BL_trimester_univ.docx"))
```
## Marginally adjusted means
```{r}
m_BL_a_mmeans_univ_t <- ggemmeans(m_BL_u_t, "trimester_real_def3")
m_BL_a_mmeans_univ_t <- mmeans_ci_vertic_cont(m_BL_a_mmeans_univ_t) 

 m_BL_a_mmeans_univ_t['outcome'] <- c("birth length (cm)")
  m_BL_a_mmeans_univ_t['trimester'] <- c("no", "first", "second", "third")

 m_BL_a_mmeans_univ_t<-m_BL_a_mmeans_univ_t[, c("outcome",'trimester', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# PI 
```{r}
  m_PI_u_t<- rlm(PI ~ trimester_real_def3, data=flu_cases_during_pregn_pandemy_trimester_livebirths)
  summary(m_PI_u_t)
  nobs(m_PI_u_t)
```
### Table
```{r}
PI_GLM3 <-  round(head(estimates_cont_rlm(m_PI_u_t),17), 2)

  PI_GLM3['Parameters'] <- c("intercept", 
                            "Flu trimester (ref: no flu)", "", ""
                            )
  PI_GLM3['category'] <- c(" ",
                          "first", "second", "third")
  PI_GLM3 <- PI_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PI_gt <- PI_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,067")
    M_PI_gt
    
M_PI_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable/rlm","M_PI_trimester_univ.docx"))
```

## Marginally adjusted means
```{r}
m_PI_a_mmeans_univ_t <- ggemmeans(m_PI_u_t, "trimester_real_def3")
m_PI_a_mmeans_univ_t <- mmeans_ci_vertic_cont(m_PI_a_mmeans_univ_t) 

 m_PI_a_mmeans_univ_t['outcome'] <- c("ponderal index")
  m_PI_a_mmeans_univ_t['trimester'] <- c("no", "first", "second", "third")

 m_PI_a_mmeans_univ_t<-m_PI_a_mmeans_univ_t[, c("outcome",'trimester', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


# Pooling the tables for marginal means
```{r}
a_m_cont_outc_univ_trim <- rbind(m_BW_a_mmeans_univ_t, m_HC_a_mmeans_univ_t, 
                                m_PW_a_mmeans_univ_t, m_BL_a_mmeans_univ_t, 
                                m_PI_a_mmeans_univ_t, m_GA_a_mmeans_univ_t)
a_m_cont_outc_univ_trim <- a_m_cont_outc_univ_trim%>%
 mutate(sex="all",
         model="univariable")
a_m_cont_outc_univ_trim%>%
  gt() %>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable/rlm", "M_cont_marg_means_Flu_in_pregn_and_in_pandemic_gt.docx"))
```

# LBW 
```{r}
 m_LBW_u_t<- glm(LBW ~ trimester_real_def3, family = "binomial", data=flu_cases_during_pregn_pandemy_trimester_livebirths)
  summary(m_LBW_u_t)
  nobs(m_LBW_u_t)
```

## Table
```{r}
LBW_GLM3 <- round(head(estimates_binary(m_LBW_u_t)), 2)

  LBW_GLM3['Parameters'] <- c("intercept", 
                            "Flu trimester (ref: no flu)", "", ""
                            )
  LBW_GLM3['category'] <- c(" ",
                          "first", "second", "third")
  LBW_GLM3<-LBW_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_LBW_gt <- LBW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,071")
    M_LBW_gt
    
LBW_estimates_gt <- M_LBW_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable", "M_LBW_trimester_univ.docx"))
```
## Marginally adjusted means
```{r}
m_LBW_a_mmeans_univ_t <- ggemmeans(m_LBW_u_t, "trimester_real_def3")
m_LBW_a_mmeans_univ_t <- mmeans_ci_vertic_bin(m_LBW_a_mmeans_univ_t) 

 m_LBW_a_mmeans_univ_t['outcome'] <- c("LBW (<2,500g)")
  m_LBW_a_mmeans_univ_t['trimester'] <- c("no", "first", "second", "third")

 m_LBW_a_mmeans_univ_t<-m_LBW_a_mmeans_univ_t[, c("outcome",'trimester', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# stillbirth 
```{r}
 m_SB_u_t<- glm(stillbirth ~ trimester_real_def3, family = binomial, data=flu_cases_during_pregn_pandemy_trimester)
  summary(m_SB_u_t)
  nobs(m_SB_u_t)
```
## Table
```{r}
SB_GLM3 <- round(head(estimates_binary(m_SB_u_t)), 2)

  SB_GLM3['Parameters'] <- c("intercept", 
                            "Flu trimester (ref: no flu)", "", ""
                            )
  SB_GLM3['category'] <- c(" ",
                          "first", "second", "third")
  SB_GLM3<-SB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_SB_gt <- SB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,163")
    M_SB_gt
    
SB_estimates_gt <- M_SB_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable", "M_SB_trimester_univ.docx"))
```

## Marginally adjusted means
```{r}
m_SB_a_mmeans_univ_t <- ggemmeans(m_SB_u_t, "trimester_real_def3")
m_SB_a_mmeans_univ_t <- mmeans_ci_vertic_bin(m_SB_a_mmeans_univ_t) 

 m_SB_a_mmeans_univ_t['outcome'] <- c("stillbirth")
  m_SB_a_mmeans_univ_t['trimester'] <- c("no", "first", "second", "third")

 m_SB_a_mmeans_univ_t<-m_SB_a_mmeans_univ_t[, c("outcome",'trimester', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# PTB 
```{r}
 m_PTB_u_t<- glm(PTB_corrected ~ trimester_real_def3, family = "binomial", data=flu_cases_during_pregn_pandemy_trimester_livebirths)
  summary(m_PTB_u_t)
  nobs(m_PTB_u_t)
```

### Table
```{r}
PTB_GLM3 <- round(head(estimates_binary(m_PTB_u_t)), 2)

  PTB_GLM3['Parameters'] <- c("intercept", 
                            "Flu trimester (ref: no flu)", "", ""
                            )
  PTB_GLM3['category'] <- c(" ",
                          "first", "second", "third")
  PTB_GLM3<-PTB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_PTB_gt <- PTB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,071")
    M_PTB_gt
    
PTB_estimates_gt <- M_PTB_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable", "M_PTB_trimester_univ.docx"))
```
### Marginal proportions
```{r}
m_PTB_a_mmeans_univ_t <- ggemmeans(m_PTB_u_t, "trimester_real_def3", margin="marginalmeans")

m_PTB_a_mmeans_univ_t <- mmeans_ci_vertic_bin(m_PTB_a_mmeans_univ_t) 

 m_PTB_a_mmeans_univ_t['outcome'] <- c("PTB (<37 weeks)")
  m_PTB_a_mmeans_univ_t['trimester'] <- c("no", "first", "second", "third")
m_PTB_a_mmeans_univ_t<-m_PTB_a_mmeans_univ_t[, c("outcome",'trimester', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Neonat mortality
```{r}
 m_NM_u_t<- glm(neonat_mort_d1_d5 ~ trimester_real_def3, family = "binomial", data=flu_cases_during_pregn_pandemy_trimester_livebirths)
  summary(m_NM_u_t)
  nobs(m_NM_u_t)
```

### Table
```{r}
NM_GLM3 <- round(head(estimates_binary(m_NM_u_t)), 2)

  NM_GLM3['Parameters'] <- c("intercept", 
                            "Flu trimester (ref: no flu)", "", ""
                            )
  NM_GLM3['category'] <- c(" ",
                          "first", "second", "third")
  NM_GLM3<-NM_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_NM_gt <- NM_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  )%>%
     tab_source_note(source_note = "n=2,070")
    M_NM_gt
    
NM_estimates_gt <- M_NM_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable", "M_NM_trimester_univ.docx"))
```

### Marginal proportions
```{r}
m_NM_a_mmeans_multiv_t <- ggemmeans(m_NM_u_t, "trimester_real_def3", margin="marginalmeans")

m_NM_a_mmeans_multiv_t <- mmeans_ci_vertic_bin(m_NM_a_mmeans_multiv_t) 

 m_NM_a_mmeans_multiv_t['outcome'] <- c("early neonatal mortality")
  m_NM_a_mmeans_multiv_t['trimester'] <- c("no", "first", "second", "third")
m_NM_a_mmeans_multiv_t<-m_NM_a_mmeans_multiv_t[, c("outcome",'trimester', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```



# Pooling the tables for marginal proportions
```{r}
a_m_bin_outc_univ_trim <- rbind(m_LBW_a_mmeans_univ_t, m_PTB_a_mmeans_univ_t,m_SB_a_mmeans_univ_t)
                                #,m_NM_a_mmeans_multiv_t # not enough cases
 a_m_bin_outc_univ_trim  <- a_m_bin_outc_univ_trim%>%
 mutate(sex="all",
         model="univariable")
a_m_bin_outc_univ_trim%>%
  gt() %>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/trimester/univariable", "M_bin_marg_prop_Flu_in_pregn_and_in_pandemic_gt.docx"))
```


