---
title: "Univariable models"
author: "Mathilde Le Vu"
date: "2024-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Gestational age 
```{r}
  m_GA_u_sev<- rlm(GA_weeks_corrected ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths)
  summary(m_GA_u_sev)
  nobs(m_GA_u_sev)
```

## Table
```{r}
GA_GLM3 <- round(head(estimates_cont_rlm(m_GA_u_sev)), 2)

  GA_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", "")
  GA_GLM3['category'] <- c(" ",
                          "mild", "severe")
  GA_GLM3<-GA_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_GA_gt <- GA_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,040")
    M_GA_gt
    
M_GA_gt%>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable/rlm", "M_GA_severity_univ.docx"))
```

## Marginally adjusted means
```{r}
m_GA_a_mmeans <- ggemmeans(m_GA_u_sev, "Grippe_severity3")
m_GA_a_mmeans <- mmeans_ci_vertic_cont(m_GA_a_mmeans) 


 m_GA_a_mmeans['outcome'] <- c("gestational age (weeks)")
  m_GA_a_mmeans['severity'] <- c("no", "mild", "severe")
   m_GA_a_mmeans<-m_GA_a_mmeans[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Birthweight 
```{r}
  m_BW_u_sev<- rlm(birthweight ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths)
  summary(m_BW_u_sev)
  nobs(m_BW_u_sev)
```

## Table
```{r}
BW_GLM3 <- round(head(estimates_cont_rlm(m_BW_u_sev)), 2)

  BW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  BW_GLM3['category'] <- c(" ",
                          "mild", "severe")
  BW_GLM3<-BW_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_BW_gt <- BW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,040")
    M_BW_gt
    
M_BW_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable/rlm", "M_BW_severity_univ.docx"))
```

## Marginally adjusted means
```{r}
m_BW_a_mmeans <- ggemmeans(m_BW_u_sev, "Grippe_severity3")
m_BW_a_mmeans <- mmeans_ci_vertic_cont(m_BW_a_mmeans) 

 m_BW_a_mmeans['outcome'] <- c("birth weight (g)")
m_BW_a_mmeans['severity'] <- c("no", "mild", "severe")
 m_BW_a_mmeans<-m_BW_a_mmeans[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Head circumference 
```{r}
m_HC_sev<- rlm(head_circ ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths)
summary(m_HC_sev)
nobs(m_HC_sev)
```

## Table
```{r}
HC_GLM3 <- round(head(estimates_cont_rlm(m_HC_sev)), 2)

  HC_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  HC_GLM3['category'] <- c(" ",
                          "mild", "severe")
  HC_GLM3 <- HC_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_HC_gt <- HC_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,032")
    M_HC_gt
    
M_HC_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable/rlm", "M_HC_severity_univ.docx"))
```

## Marginally adjusted means
```{r}
m_HC_a_mmeans <- ggemmeans(m_HC_sev, "Grippe_severity3")
m_HC_a_mmeans <- mmeans_ci_vertic_cont(m_HC_a_mmeans) 

 m_HC_a_mmeans['outcome'] <- c("head circumference (cm)")
  m_HC_a_mmeans['severity'] <- c("no", "mild", "severe")
 m_HC_a_mmeans<-m_HC_a_mmeans[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Placenta weight 
```{r}
  m_PW_sev<- rlm(placentaweight ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths)
  summary(m_PW_sev)
  nobs(m_PW_sev)
```

## Table
```{r}
PW_GLM3 <- round(head(estimates_cont_rlm(m_PW_sev)), 2)

  PW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  PW_GLM3['category'] <- c(" ",
                          "mild", "severe")
  PW_GLM3 <- PW_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PW_gt <- PW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,014")
    M_PW_gt
    
M_PW_gt%>%
    gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable/rlm", "M_PW_severity_univ.docx"))
```

## Marginally adjusted means
```{r}
m_PW_a_mmeans <- ggemmeans(m_PW_sev, "Grippe_severity3")
m_PW_a_mmeans <- mmeans_ci_vertic_cont(m_PW_a_mmeans) 

 m_PW_a_mmeans['outcome'] <- c("placenta weight (g)")
   m_PW_a_mmeans['severity'] <- c("no","mild", "severe")
  m_PW_a_mmeans<-m_PW_a_mmeans[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Birth length 
```{r}
  m_BL_sev<- rlm(babylength ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths)
  summary(m_BL_sev)
  nobs(m_BL_sev)
```

## Table
```{r}
BL_GLM3 <- round(head(estimates_cont_rlm(m_BL_sev)), 2)

  BL_GLM3['Parameters'] <- c("intercept", 
                           "Flu severity (ref: no flu)", ""
                            )
  BL_GLM3['category'] <- c(" ",
                          "mild", "severe")
  BL_GLM3 <- BL_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_BL_gt <- BL_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,036")
    M_BL_gt
    
M_BL_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable/rlm", "M_BL_severity_univ.docx"))
```

## Marginally adjusted means
```{r}
m_BL_a_mmeans <- ggemmeans(m_BL_sev, "Grippe_severity3")
m_BL_a_mmeans <- mmeans_ci_vertic_cont(m_BL_a_mmeans) 

 m_BL_a_mmeans['outcome'] <- c("birth length (cm)")
   m_BL_a_mmeans['severity'] <- c("no", "mild", "severe")
   m_BL_a_mmeans<-m_BL_a_mmeans[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# PI 
```{r}
  m_PI_sev<- rlm(PI ~ Grippe_severity3, data=flu_cases_during_pregn_pandemy_sev_livebirths)
  summary(m_PI_sev)
  nobs(m_PI_sev)
```

## Table
```{r}
PI_GLM3 <- round(head(estimates_cont_rlm(m_PI_sev)), 2)

  PI_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  PI_GLM3['category'] <- c(" ",
                          "mild", "severe")
  PI_GLM3 <- PI_GLM3[, c('Parameters', "category", "beta", "lci","uci")]

   M_PI_gt <- PI_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,036")
    M_PI_gt
    
M_PI_gt%>%
    gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable/rlm", "M_PI_severity_univ.docx"))
```

## Marginally adjusted means
```{r}
m_PI_a_mmeans <- ggemmeans(m_PI_sev, "Grippe_severity3", margin="marginalmeans")
m_PI_a_mmeans <- mmeans_ci_vertic_cont(m_PI_a_mmeans) 

 m_PI_a_mmeans['outcome'] <- c("ponderal index")
    m_PI_a_mmeans['severity'] <- c("no", "mild", "severe")
  m_PI_a_mmeans<-m_PI_a_mmeans[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Pooling the tables for predicted means together
```{r}
a_m_cont_outc_sev_u <- rbind(m_BW_a_mmeans, m_HC_a_mmeans, 
                             m_PW_a_mmeans, m_BL_a_mmeans,
                             m_PI_a_mmeans, m_GA_a_mmeans)
a_m_cont_outc_sev_u <- a_m_cont_outc_sev_u %>%
  mutate(mean=round(mean, 2),
         lci=round(lci, 2),
         uci=round(uci, 2),
         sex="all",
         model="univariable")
a_m_cont_outc_sev_u%>%
  gt() %>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable/rlm", "M_cont_estimates_Flu_severity_univ_gt.docx"))
```

# LBW 
```{r}
 m_LBW_sev<- glm(LBW ~ Grippe_severity3, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths)
  summary(m_LBW_sev)
  nobs(m_LBW_sev)
```

## Table
```{r}
LBW_GLM3 <- round(head(estimates_binary(m_LBW_sev)), 2)

  LBW_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  LBW_GLM3['category'] <- c(" ",
                          "mild", "severe")
  LBW_GLM3<-LBW_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_LBW_gt <- LBW_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,040")
    M_LBW_gt
    
LBW_estimates_gt <- M_LBW_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable", "M_LBW_severity_univ.docx"))
```

## Marginal proportions
```{r}
m_LBW_a_mmeans_u <- ggemmeans(m_LBW_sev, "Grippe_severity3", margin="marginalmeans")
m_LBW_a_mmeans_u <- mmeans_ci_vertic_bin(m_LBW_a_mmeans_u) 

 m_LBW_a_mmeans_u['outcome'] <- c("LBW (<2,500g)")
 m_LBW_a_mmeans_u['severity'] <- c("no", "mild", "severe")
  m_LBW_a_mmeans_u<-m_LBW_a_mmeans_u[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


# Stillbirth 
```{r}
 m_SB_sev<- glm(stillbirth ~ Grippe_severity3, family = binomial, data=flu_cases_during_pregn_pandemy_sev)
  summary(m_SB_sev)
  nobs(m_SB_sev)
```

## Table
```{r}
SB_GLM3 <- round(head(estimates_binary(m_SB_sev)), 2)

  SB_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  SB_GLM3['category'] <- c(" ",
                          "mild", "severe")
  SB_GLM3<-SB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_SB_gt <- SB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,132")
    M_SB_gt
    
SB_estimates_gt <- M_SB_gt%>%
   gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable", "M_SB_severity_univ.docx"))
```

## Marginal proportions
```{r}
m_SB_a_mmeans_u <- ggemmeans(m_SB_sev, "Grippe_severity3", margin="marginalmeans")
m_SB_a_mmeans_u <- mmeans_ci_vertic_bin(m_SB_a_mmeans_u) 

 m_SB_a_mmeans_u['outcome'] <- c("stillbirth")
  m_SB_a_mmeans_u['severity'] <- c("no", "mild", "severe")

  m_SB_a_mmeans_u<-m_SB_a_mmeans_u[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


# PTB 
```{r}
 m_PTB_sev<- glm(PTB_corrected ~ Grippe_severity3, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths)
  summary(m_PTB_sev)
  nobs(m_PTB_sev)
```

## Table
```{r}
PTB_GLM3 <- round(head(estimates_binary(m_PTB_sev)), 2)

  PTB_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  PTB_GLM3['category'] <- c(" ",
                          "mild", "severe")
  PTB_GLM3<-PTB_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_PTB_gt <- PTB_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  ) %>%
     tab_source_note(source_note = "n=2,040")
    M_PTB_gt
    
PTB_estimates_gt <- M_PTB_gt%>%
    gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable", "M_PTB_severity_univ.docx"))
```

## Marginal proportions
```{r}
m_PTB_a_mmeans_u <- ggemmeans(m_PTB_sev, "Grippe_severity3", margin="marginalmeans")
m_PTB_a_mmeans_u <- mmeans_ci_vertic_bin(m_PTB_a_mmeans_u) 

 m_PTB_a_mmeans_u['outcome'] <- c("PTB (<37 weeks)")
  m_PTB_a_mmeans_u['severity'] <- c("no", "mild", "severe")

  m_PTB_a_mmeans_u<-m_PTB_a_mmeans_u[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```

# Neonat mortality
```{r}
 m_NM_sev<- glm(neonat_mort_d1_d5 ~ Grippe_severity3, family = "binomial", data=flu_cases_during_pregn_pandemy_sev_livebirths)
  summary(m_NM_sev)
  nobs(m_NM_sev)
```

## Table
```{r}
NM_GLM3 <- round(head(estimates_binary(m_NM_sev)), 2)

  NM_GLM3['Parameters'] <- c("intercept", 
                            "Flu severity (ref: no flu)", ""
                            )
  NM_GLM3['category'] <- c(" ",
                          "mild", "severe")
  NM_GLM3<-NM_GLM3[, c('Parameters', "category", "OR", "lci","uci")]

   M_NM_gt <- NM_GLM3 %>%
      gt()%>%
      tab_spanner(label = "95% CI", columns = c(lci, uci),
                  ) %>%
  tab_options(table.width = pct(18), data_row.padding = px(2),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14
  )%>%
     tab_source_note(source_note = "n=2,039")
    M_NM_gt
    
NM_estimates_gt <- M_NM_gt%>%
    gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable","M_NM_severity_univ.docx"))
```

## Marginal proportions
```{r}
m_NM_a_mmeans_u <- ggemmeans(m_NM_sev, "Grippe_severity3", margin="marginalmeans")
m_NM_a_mmeans_u <- mmeans_ci_vertic_bin(m_NM_a_mmeans_u) 

 m_NM_a_mmeans_u['outcome'] <- c("early neonatal mortality")
  m_NM_a_mmeans_u['severity'] <- c("no", "mild", "severe")
 m_NM_a_mmeans_u<-m_NM_a_mmeans_u[, c("outcome",'severity', "mean","lci", "uci", 
                                    "d", "lower_diff", "upper_diff")]
```


# Pooling the tables for marginal proportions
```{r}
a_m_bin_outc_sev_u <- rbind(m_LBW_a_mmeans_u, m_PTB_a_mmeans_u,
m_SB_a_mmeans_u)
#, m_NM_a_mmeans_u)
a_m_bin_outc_sev_u <- a_m_bin_outc_sev_u %>%
  mutate(sex="all",
         model="univariable")
a_m_bin_outc_sev_u%>%
  gt() %>%
  gtsave(here("output/tables/models_flu_trimester_or_severity/severity/univariable", "M_bin_marg_prop_Flu_severityuniv_gt.docx"))
```




